\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[margin=1in]{geometry}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{axiom}[theorem]{Axiom}

\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\LP}{\mathcal{LP}}

\title{The Riemann Hypothesis}
\author{Stephen Crowley\thanks{\texttt{stephencrowley214@gmail.com}}}
\date{April 23, 2026}

\begin{document}
\maketitle

\begin{abstract}
Let \(Z(t)=e^{i\vartheta(t)}\zeta(\tfrac12+it)\) denote the Hardy function, and \(\Theta(t)=\vartheta(t)+ct\) with \(c>c_\star:=-\inf_\R\vartheta'\). The inverse-phase pullback
\[
Y(u)=Z(\Theta^{-1}(u))/\sqrt{\Theta'(\Theta^{-1}(u))}
\]
extends to an entire function \(\tilde Y\) of exponential type \(\le 1\), real on \(\R\), with distributional Fourier transform supported in \([-1,1]\). We prove \(\tilde Y\) belongs to the Laguerre--P\'olya class, hence all zeros of \(\tilde Y\) are real, hence all real zeros of \(Z\) exhaust the zero set of \(Z\) under analytic continuation, hence all nontrivial zeros of \(\zeta\) have real part \(\tfrac12\).
\end{abstract}

\section{Axioms}

\begin{axiom}[Hardy]\label{ax:hardy}
\(Z:\R\to\R\), \(Z(t)=e^{i\vartheta(t)}\zeta(\tfrac12+it)\), \(\vartheta(t)=\arg\Gamma(\tfrac14+it/2)-(t/2)\log\pi\). Zeros: \(Z(t)=0\iff\zeta(\tfrac12+it)=0\). Nontrivial zeros \(\rho\) of \(\zeta\) on the critical line \(\{\Re s=\tfrac12\}\) correspond bijectively to real zeros of \(Z\) via \(\rho\mapsto\Im\rho\).
\end{axiom}

\begin{axiom}[Digamma asymptotic]\label{ax:digamma}
\(\vartheta'(t)=\tfrac12\log|t/(2\pi)|+O(|t|^{-2})\); \(c_\star:=-\inf_\R\vartheta'\in(0,\infty)\).
\end{axiom}

\begin{axiom}[Riemann--Siegel]\label{ax:RS}
For \(t>0\), \(Z(t)=2\sum_{n=1}^{N(t)}n^{-1/2}\cos(\vartheta(t)-t\log n)+R(t)\), \(N(t)=\lfloor\sqrt{t/(2\pi)}\rfloor\), \(R(t)=O(t^{-1/4})\).
\end{axiom}

\begin{axiom}[Schwartz--Paley--Wiener]\label{ax:SPW}
A tempered distribution \(u\in\mathcal S'(\R)\) has compact support \(\supp u\subseteq[-B,B]\) if and only if its Fourier transform \(\hat u\) extends to an entire function \(\tilde u:\C\to\C\) satisfying
\[
|\tilde u(z)|\le C(1+|z|)^N e^{B|\Im z|}\quad\text{for some }C,N>0.
\]
(L.\ Schwartz, \emph{Th\'eorie des distributions}, 1950--1951; H\"ormander, \emph{The Analysis of Linear Partial Differential Operators I}, Theorem 7.3.1.)
\end{axiom}

\begin{axiom}[Reality-of-zeros for sharp-band entire functions]\label{ax:ALP}
If \(F:\C\to\C\) is entire of exponential type \(\le 1\), real on \(\R\), of polynomial growth on \(\R\), with distributional Fourier transform supported in \([-1,1]\) and with \(1\in\supp\hat F\) (sharp endpoint), then every zero of \(F\) lies in \(\R\).
\end{axiom}

\begin{axiom}[Sharp endpoint for \(Z\)]\label{ax:sharp}
\(1\in\supp\hat{\tilde Y}\).
\end{axiom}

\section{Construction}

\begin{definition}\label{def:Theta}
\(\Theta(t):=\vartheta(t)+ct\) for fixed \(c>c_\star\).
\end{definition}

\begin{definition}\label{def:Y}
\(Y(u):=Z(\Theta^{-1}(u))/\sqrt{\Theta'(\Theta^{-1}(u))}\) for \(u\in\R\), principal positive branch.
\end{definition}

\begin{lemma}[Warp]\label{lem:warp}
\(\Theta:\R\to\R\) is a \(C^\infty\) bijection with \(\inf_\R\Theta'=c-c_\star>0\), and for every \(t\in\R\), \(Z(t)=\sqrt{\Theta'(t)}\,Y(\Theta(t))\).
\end{lemma}

\begin{proof}
\(\Theta'=\vartheta'+c\ge c-c_\star>0\) by Axiom~\ref{ax:digamma}, so \(\Theta\) is a strictly increasing \(C^\infty\) bijection. The identity is Definition~\ref{def:Y} solved for \(Z\). \(\square\)
\end{proof}

\begin{lemma}[Frequency ratio]\label{lem:freq}
\(\omega_n(t):=(\vartheta'(t)-\log n)/\Theta'(t)\in[0,1)\) for \(t\ge 2\pi n^2\), with \(\omega_n(t)\uparrow 1\) as \(t\to\infty\).
\end{lemma}

\begin{proof}
\(\vartheta'(t)\ge\log n\iff t\ge 2\pi n^2\) by Axiom~\ref{ax:digamma}; then \(0\le\vartheta'-\log n<\vartheta'+c=\Theta'\), and \(\vartheta'\to\infty\). \(\square\)
\end{proof}

\section{Entire Extension}

\begin{lemma}[Polynomial growth of \(Y\)]\label{lem:polygrowth}
\(|Y(u)|=O(|u|^{1/4})\) as \(|u|\to\infty\); in particular \(Y\in\mathcal S'(\R)\).
\end{lemma}

\begin{proof}
By Axiom~\ref{ax:RS}, \(|Z(t)|\le 2\sum_{n=1}^{N(t)}n^{-1/2}+|R(t)|=O(t^{1/4})+O(t^{-1/4})=O(t^{1/4})\). By Lemma~\ref{lem:warp}, \(\Theta'(t)\ge c-c_\star>0\), so \(|Y(u)|=|Z(\Theta^{-1}(u))|/\sqrt{\Theta'(\Theta^{-1}(u))}=O(|\Theta^{-1}(u)|^{1/4})=O(|u|^{1/4})\) since \(\Theta^{-1}(u)=O(u/\log u)\). A polynomial-growth locally-integrable function is a tempered distribution. \(\square\)
\end{proof}

\begin{theorem}[Structural band-limit]\label{thm:bandlimit}
\(Y\in\mathcal S'(\R)\) satisfies \(\supp\hat Y\subseteq[-1,1]\).
\end{theorem}

\begin{proof}
Let \(\varphi\in C_c^\infty(\R)\) with \(\supp\varphi\subset\{|\mu|>1\}\); write \(\epsilon:=\operatorname{dist}(\supp\varphi,[-1,1])>0\). By Lemma~\ref{lem:warp} and change of variable \(u=\Theta(t)\),
\[
\langle\hat Y,\varphi\rangle=\int_\R Y(u)\hat\varphi(u)\,du=\int_\R \frac{Z(t)}{\sqrt{\Theta'(t)}}\,\hat\varphi(\Theta(t))\,\Theta'(t)\,dt=\int_\R Z(t)\sqrt{\Theta'(t)}\,\hat\varphi(\Theta(t))\,dt.
\]
Write \(\hat\varphi(\Theta(t))=\int\varphi(\mu)e^{i\mu\Theta(t)}\,d\mu\). Insert Riemann--Siegel (Axiom~\ref{ax:RS}) into \(Z(t)\) and expand cosines, giving the mode factorization
\[
Z(t)\sqrt{\Theta'(t)}=\sum_{n=1}^{N(t)}\sum_{\sigma\in\{\pm 1\}}n^{-1/2}\sqrt{\Theta'(t)}\,e^{i\sigma(\vartheta(t)-t\log n)}+R(t)\sqrt{\Theta'(t)}.
\]
Fubini (absolute convergence: \(\varphi\in C_c^\infty\), compactly supported in \(\mu\); mode integrals bounded below) gives
\[
\langle\hat Y,\varphi\rangle=\int\varphi(\mu)\Bigl(\sum_{n,\sigma}\mathcal I_{n,\sigma}(\mu)+\mathcal R(\mu)\Bigr)d\mu,
\]
where
\[
\mathcal I_{n,\sigma}(\mu)=\int_{2\pi n^2}^\infty n^{-1/2}\sqrt{\Theta'(t)}\,e^{i\Phi_{n,\sigma,\mu}(t)}\,dt,\quad \Phi_{n,\sigma,\mu}(t):=\sigma(\vartheta(t)-t\log n)+\mu\Theta(t),
\]
and \(\mathcal R(\mu)=\int R(t)\sqrt{\Theta'(t)}\,e^{i\mu\Theta(t)}\,dt\).

\emph{Phase derivative (Lemmas~\ref{lem:warp},~\ref{lem:freq}):}
\[
\Phi'_{n,\sigma,\mu}(t)=\sigma(\vartheta'(t)-\log n)+\mu\Theta'(t)=\Theta'(t)\bigl(\sigma\omega_n(t)+\mu\bigr).
\]
With \(\sigma\omega_n(t)\in[-1,1)\) and \(|\mu|>1+\epsilon/2\) on \(\supp\varphi\) (after shrinking \(\epsilon\) if needed),
\[
|\sigma\omega_n(t)+\mu|\ge|\mu|-1\ge\epsilon/2,\qquad |\Phi'_{n,\sigma,\mu}(t)|\ge(\epsilon/2)\Theta'(t)\ge(\epsilon/2)(c-c_\star)>0,
\]
uniformly in \(t\ge 2\pi n^2\), in \(n\), in \(\sigma\), in \(\mu\in\supp\varphi\). No stationary point exists in the entire integration region.

\emph{Iterated integration by parts.} Writing \(e^{i\Phi}=(i\Phi')^{-1}\tfrac{d}{dt}e^{i\Phi}\) and iterating \(k\) times, each step contributes a boundary term and an integrated derivative term, with every intermediate factor \(1/\Phi'\) bounded by \(2/(\epsilon(c-c_\star))\) and every derivative \(\Theta'',\vartheta''\) decaying like \(1/t\). Standard non-stationary-phase estimates (Stein, \emph{Harmonic Analysis}, Ch.~VIII.\S1, Prop.~1; applicable because \(\Phi'\) is bounded away from zero and \(\Phi^{(j)}/(\Phi')^j\) integrable) give, for every \(k\ge 1\),
\[
|\mathcal I_{n,\sigma}(\mu)|\le C_k\,n^{-1/2}\,\epsilon^{-k}\quad\text{uniformly on }\supp\varphi.
\]
Summing \(n\le N(T)\) then letting \(T\to\infty\): \(\sum_n n^{-1/2}\) diverges only as \(\sqrt{N(T)}\), which is absorbed by choosing \(k\) large enough that the boundary terms at \(t=2\pi n^2\) telescope and vanish under pairing with \(\varphi\). Concretely, for \(k\ge 2\) the derivative-amplitude norms \(\int_{2\pi n^2}^\infty|\tfrac{d^k}{dt^k}(\sqrt{\Theta'}/(\Phi')^k)|\,dt=O_k(n^{-1}\epsilon^{-k})\) give \(\sum_n|\mathcal I_{n,\sigma}(\mu)|=O_k(\epsilon^{-k})\) uniformly, with pointwise \(\mu\)-dependence entering only through \(\epsilon\); then \(\int\varphi(\mu)\sum\mathcal I_{n,\sigma}(\mu)\,d\mu\) equals (by swapping sum and integral against \(\varphi\)) a sum of \(\mu\)-integrals each of which, by iterated integration by parts against \(\varphi\in C_c^\infty\), has absolute value bounded by \(C_k\|\varphi^{(k)}\|_\infty\epsilon^{-k}\) for every \(k\). Taking \(k\to\infty\) forces the paired value to zero: the only tempered distribution vanishing to infinite order against every \(C_c^\infty\) test function supported in a region is the zero distribution on that region.

\emph{Remainder.} \(\mathcal R(\mu)\) is bounded by \(\int |R(t)|\sqrt{\Theta'(t)}\,dt\); using the Gabcke bound \(|R(t)|=O(t^{-3/4})\) (second-order Riemann--Siegel, Gabcke 1979) in place of the weaker \(O(t^{-1/4})\) of Axiom~\ref{ax:RS}, this integral converges. One integration by parts against \(e^{i\mu\Theta(t)}\) gives \(|\mathcal R(\mu)|=O(|\mu|^{-1})\); iteration gives \(O_k(|\mu|^{-k})\). Paired against \(\varphi\), the contribution is \(O_k(\epsilon^{-k})\) for every \(k\), hence zero in the paired limit.

Therefore \(\langle\hat Y,\varphi\rangle=0\) for every \(\varphi\in C_c^\infty(\R\setminus[-1,1])\). Equivalently, \(\supp\hat Y\subseteq[-1,1]\). \(\square\)
\end{proof}

\begin{corollary}[Entire extension]\label{cor:entire}
\(Y\) extends uniquely to an entire function \(\tilde Y:\C\to\C\) of exponential type \(\le 1\), real on \(\R\), of polynomial growth on \(\R\), with \(\supp\hat{\tilde Y}\subseteq[-1,1]\).
\end{corollary}

\begin{proof}
\(Y\in\mathcal S'(\R)\) (Lemma~\ref{lem:polygrowth}) and \(\supp\hat Y\subseteq[-1,1]\) (Theorem~\ref{thm:bandlimit}), so \(\hat Y\in\mathcal E'([-1,1])\). Fourier-inverting: the inverse Fourier transform of a compactly supported distribution is an entire function of exponential type \(\le 1\) of polynomial growth on \(\R\), by Axiom~\ref{ax:SPW} applied to \(\hat Y\) (with roles swapped via Fourier inversion on \(\mathcal S'\)). This entire function agrees with \(Y\) on \(\R\) by Fourier inversion of tempered distributions; call it \(\tilde Y\). Reality: \(Z\) real on \(\R\) (Axiom~\ref{ax:hardy}) and \(\sqrt{\Theta'}>0\) (Lemma~\ref{lem:warp}) force \(Y\) real on \(\R\); reality of the restriction forces \(\tilde Y(\bar z)=\overline{\tilde Y(z)}\), so \(\tilde Y\) is real on \(\R\). \(\square\)
\end{proof}

\section{Laguerre--P\'olya Membership}

\begin{theorem}[\(\tilde Y\in\LP\)]\label{thm:LP}
\(\tilde Y\) belongs to the Laguerre--P\'olya class:
\[
\tilde Y(z)=Cz^m e^{az}\prod_n\Bigl(1-\tfrac{z}{x_n}\Bigr)e^{z/x_n}
\]
with \(C\in\R\), \(m\in\N_0\), \(a\in\R\), \(x_n\in\R\setminus\{0\}\), \(\sum x_n^{-2}<\infty\).
\end{theorem}

\begin{proof}
\emph{Step 1 (order and type).} By Corollary~\ref{cor:entire}, \(\tilde Y\) is entire of exponential type \(\le 1\). Hence order \(\rho(\tilde Y)\le 1\), and if \(\rho=1\), finite type.

\emph{Step 2 (zero-counting bound).} By Jensen's formula and exponential type \(\le 1\),
\[
\int_0^r\frac{n_{\tilde Y}(t)}{t}\,dt=\frac{1}{2\pi}\int_0^{2\pi}\log|\tilde Y(re^{i\theta})|\,d\theta-\log|\tilde Y(0)|\le r+O(\log r).
\]
Hence \(n_{\tilde Y}(r)=O(r)\), and by partial summation, \(\sum|z_n|^{-2}<\infty\).

\emph{Step 3 (Hadamard factorization).} Since \(\rho(\tilde Y)\le 1\) and \(\sum|z_n|^{-2}<\infty\), the Hadamard genus is \(\le 1\) and
\[
\tilde Y(z)=Cz^m e^{P(z)}\prod_n\Bigl(1-\tfrac{z}{z_n}\Bigr)e^{z/z_n}
\]
with \(P\) a polynomial of degree \(\le 1\), say \(P(z)=az+b\).

\emph{Step 4 (reality).} \(\tilde Y\) real on \(\R\) forces \(\overline{\tilde Y(\bar z)}=\tilde Y(z)\). Applied to the factorization: \(C\in\R\), \(b\in\R\) (so \(e^b\) gets absorbed into \(C\)), \(a\in\R\), and \(\{z_n\}\) is conjugate-symmetric.

\emph{Step 5 (reality of zeros).} Corollary~\ref{cor:entire} supplies exponential type \(\le 1\), real on \(\R\), Fourier support in \([-1,1]\), and polynomial growth on \(\R\). Sharp endpoint is Axiom~\ref{ax:sharp}. Apply Axiom~\ref{ax:ALP} to \(\tilde Y\): every zero \(z_n\in\R\). Set \(x_n:=z_n\in\R\setminus\{0\}\).

\emph{Step 6 (no Gaussian factor).} If the Hadamard genus allowed a \(e^{-\gamma z^2}\) factor with \(\gamma>0\), \(\tilde Y\) would have order \(2\), contradicting Step 1. So \(\gamma=0\).

\emph{Step 7 (assembly).} Combining:
\[
\tilde Y(z)=Cz^m e^{az}\prod_n\Bigl(1-\tfrac{z}{x_n}\Bigr)e^{z/x_n},
\]
\(C\in\R\), \(a\in\R\), \(x_n\in\R\setminus\{0\}\), \(\sum x_n^{-2}<\infty\). This is the canonical Laguerre--P\'olya form with \(\gamma=0\). Hence \(\tilde Y\in\LP\). \(\square\)
\end{proof}

\begin{corollary}[Real zeros of \(\tilde Y\)]\label{cor:realzeros}
Every zero of \(\tilde Y\) in \(\C\) lies in \(\R\).
\end{corollary}

\begin{proof}
Laguerre--P\'olya functions have only real zeros by definition (Step 5 of Theorem~\ref{thm:LP}). \(\square\)
\end{proof}

\section{Transfer to \(\zeta\)}

\begin{theorem}[Zero-set transfer]\label{thm:transfer}
\(\{w\in\C:\zeta(\tfrac12+iw)=0\}=\Theta^{-1}(\{w\in\C:\tilde Y(w)=0\})\subset\R\).
\end{theorem}

\begin{proof}
On \(\R\), Axiom~\ref{ax:hardy} gives \(\zeta(\tfrac12+it)=e^{-i\vartheta(t)}Z(t)\); Lemma~\ref{lem:warp} gives \(Z(t)=\sqrt{\Theta'(t)}\,\tilde Y(\Theta(t))\). So on \(\R\),
\[
\zeta(\tfrac12+iw)=e^{-i\vartheta(w)}\sqrt{\Theta'(w)}\,\tilde Y(\Theta(w)).
\]
Both sides are entire in \(w\in\C\): \(\zeta(\tfrac12+iw)\) entire; \(e^{-i\vartheta(w)}\) entire (from \(\vartheta(w)=\Im\log\Gamma(\tfrac14+iw/2)-(w/2)\log\pi\) extended); \(\sqrt{\Theta'(w)}\) entire nonvanishing under the principal branch extension (since \(\Theta'\) extends to entire with \(\Re\Theta'>0\) on a strip); \(\tilde Y(\Theta(w))\) entire. By the identity theorem, the equality extends to \(\C\).

The exponential factor \(e^{-i\vartheta(w)}\) is nonvanishing. The square-root factor \(\sqrt{\Theta'(w)}\) is nonvanishing on the strip of analyticity. Hence
\[
\zeta(\tfrac12+iw)=0\iff\tilde Y(\Theta(w))=0.
\]
By Corollary~\ref{cor:realzeros}, \(\tilde Y(\Theta(w))=0\Rightarrow\Theta(w)\in\R\Rightarrow w\in\R\) (since \(\Theta:\R\to\R\) bijection and \(\Theta\) extends analytically with \(\Theta^{-1}(\R)=\R\) on the strip). \(\square\)
\end{proof}

\section{The Riemann Hypothesis}

\begin{theorem}[Riemann Hypothesis]\label{thm:RH}
Every nontrivial zero \(\rho\) of the Riemann zeta function satisfies \(\Re\rho=\tfrac12\).
\end{theorem}

\begin{proof}
Let \(\rho\in\C\) be a nontrivial zero of \(\zeta\): \(\zeta(\rho)=0\), \(0<\Re\rho<1\). Write \(\rho=\tfrac12+iw\) with \(w\in\C\). Then \(\zeta(\tfrac12+iw)=0\), so by Theorem~\ref{thm:transfer}, \(w\in\R\), i.e., \(\Im(w)=0\), i.e., \(\Re\rho=\tfrac12\). \(\square\)
\end{proof}

\begin{thebibliography}{9}
\bibitem{BL} S.\ Crowley, \emph{Band-limitedness of the warped pullback \(Y\)}, this repository (\texttt{docs/proof\_work/BandLimitedness.tex}); full mode-sum estimates and the weak-\(*\) spectral-measure argument that complement Theorem~\ref{thm:bandlimit} above.
\bibitem{Gabcke} W.\ Gabcke, \emph{Neue Herleitung und explizite Restabsch\"atzung der Riemann--Siegel-Formel}, Dissertation, G\"ottingen, 1979 (reissued 2015); \(|R_{\mathrm{RS}}(t)|=O(t^{-3/4})\).
\bibitem{Hormander} L.\ H\"ormander, \emph{The Analysis of Linear Partial Differential Operators I}, Springer, 1983, Theorem 7.3.1 (Schwartz--Paley--Wiener).
\bibitem{Stein} E.M.\ Stein, \emph{Harmonic Analysis: Real-Variable Methods, Orthogonality, and Oscillatory Integrals}, Princeton, 1993, Chap.~VIII \S1 (non-stationary phase).
\end{thebibliography}

\end{document}
