\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumitem}

\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}

\title{Unitary Bijections, Measure Preservation, and $L^2$ Norm Conservation}
\author{Anonymous}
\date{July 30, 2025}

\begin{document}

\maketitle

\section{Introduction}

This document establishes the fundamental relationship between unitary bijections in $L^2$ spaces and measure-preserving transformations in ergodic theory. The central result demonstrates that $L^2$ norm preservation under bijective transformations of unbounded domains necessarily involves specific scaling factors derived from the transformation's differential structure.

\section{Bijective Transformations on Unbounded Domains}

\begin{theorem}[Bijectivity of Strictly Increasing Functions on Unbounded Domains]
\label{thm:bijective_unbounded}
Let $g: I \to \mathbb{R}$ be a strictly increasing function where $I \subseteq \mathbb{R}$ is an unbounded interval. Then $g$ is bijective onto its range $J = g(I)$, and $J$ is also an unbounded interval.
\end{theorem}

\begin{proof}
Since $g$ is strictly increasing, injectivity is immediate. For any $x_1, x_2 \in I$ with $x_1 < x_2$, one has $g(x_1) < g(x_2)$.

For surjectivity onto $J = g(I)$, let $y \in J$. By definition, there exists $x \in I$ such that $g(x) = y$. The uniqueness of such $x$ follows from injectivity.

To establish that $J$ is unbounded, consider two cases:
\begin{enumerate}
\item If $I = (a, \infty)$ or $I = [a, \infty)$ for some $a \in \mathbb{R}$, then as $x \to \infty$, since $g$ is strictly increasing, either $g(x) \to \infty$ or $g(x)$ approaches some finite supremum. If the latter held, then by the intermediate value theorem and strict monotonicity, $g$ would map $(a, \infty)$ to some bounded interval, contradicting the strict increase property over an unbounded domain.

\item If $I = (-\infty, b)$ or $I = (-\infty, b]$, a similar argument shows $J$ extends to $-\infty$.

\item If $I = \mathbb{R}$, then $J$ must be unbounded in both directions.
\end{enumerate}

Therefore, $g: I \to J$ is bijective with both $I$ and $J$ unbounded intervals.
\end{proof}

\begin{theorem}[Differentiable Bijections with Positive Derivative]
\label{thm:diff_bijective}
Let $g: I \to J$ be a $C^1$ bijection between unbounded intervals $I, J \subseteq \mathbb{R}$ such that $g'(y) > 0$ for all $y \in I$ except possibly on a set of measure zero. Then $g$ is a well-defined change of variables for Lebesgue integration.
\end{theorem}

\begin{proof}
The condition $g'(y) > 0$ almost everywhere ensures that $g$ is locally invertible almost everywhere. Since $g$ is already assumed bijective and $C^1$, the standard change of variables formula applies:

\begin{equation}
\label{eq:change_vars}
\int_J f(x) \, dx = \int_I f(g(y)) |g'(y)| \, dy = \int_I f(g(y)) g'(y) \, dy
\end{equation}

where the last equality uses $g'(y) > 0$ almost everywhere. The points where $g'(y) = 0$ form a set of measure zero and do not affect the integral.
\end{proof}

\section{$L^2$ Norm Preservation}

\begin{definition}[Scaled Transformation Operator]
\label{def:scaled_transform}
Let $g: I \to J$ be a $C^1$ bijection between unbounded intervals with $g'(y) > 0$ almost everywhere. For $f \in L^2(J, dx)$, define the scaled transformation operator $T_g$ by:
\begin{equation}
\label{eq:scaled_transform}
(T_g f)(y) = f(g(y)) \sqrt{g'(y)}
\end{equation}
\end{definition}

\begin{theorem}[$L^2$ Norm Preservation for Unbounded Domains]
\label{thm:l2_preservation}
Under the conditions of Definition~\ref{def:scaled_transform}, the operator $T_g: L^2(J, dx) \to L^2(I, dy)$ is an isometric isomorphism. Specifically:
\begin{equation}
\label{eq:norm_equality}
\|T_g f\|_{L^2(I, dy)} = \|f\|_{L^2(J, dx)}
\end{equation}
\end{theorem}

\begin{proof}
For $f \in L^2(J, dx)$, compute directly:
\begin{align}
\|T_g f\|_{L^2(I, dy)}^2 &= \int_I |f(g(y)) \sqrt{g'(y)}|^2 \, dy \label{eq:norm_calc1}\\
&= \int_I |f(g(y))|^2 g'(y) \, dy \label{eq:norm_calc2}
\end{align}

By the change of variables formula from Theorem~\ref{thm:diff_bijective} with $x = g(y)$:
\begin{equation}
\label{eq:change_vars_apply}
\int_I |f(g(y))|^2 g'(y) \, dy = \int_J |f(x)|^2 \, dx = \|f\|_{L^2(J, dx)}^2
\end{equation}

Since both $I$ and $J$ are unbounded, the change of variables is justified by approximating with bounded subintervals and applying the monotone convergence theorem.

Therefore:
\begin{equation}
\label{eq:final_norm}
\|T_g f\|_{L^2(I, dy)} = \|f\|_{L^2(J, dx)}
\end{equation}

The fact that $T_g f \in L^2(I, dy)$ follows immediately from equation~\eqref{eq:final_norm} and the assumption $f \in L^2(J, dx)$.
\end{proof}

\begin{theorem}[Necessity of Square Root Scaling]
\label{thm:necessity}
Let $g: I \to J$ be as in Theorem~\ref{thm:l2_preservation}. If $\phi: I \to \mathbb{R}^+$ is any measurable function such that $f(g(y))\phi(y) \in L^2(I, dy)$ and
\begin{equation}
\label{eq:general_norm}
\|f(g(\cdot))\phi(\cdot)\|_{L^2(I, dy)} = \|f\|_{L^2(J, dx)}
\end{equation}
for all $f \in L^2(J, dx)$, then $\phi(y) = \sqrt{g'(y)}$ almost everywhere.
\end{theorem}

\begin{proof}
From the norm condition in equation~\eqref{eq:general_norm}:
\begin{equation}
\label{eq:phi_condition}
\int_I |f(g(y))|^2 \phi(y)^2 \, dy = \int_J |f(x)|^2 \, dx
\end{equation}

Using the change of variables $x = g(y)$ on the right side:
\begin{equation}
\label{eq:phi_comparison}
\int_I |f(g(y))|^2 \phi(y)^2 \, dy = \int_I |f(g(y))|^2 g'(y) \, dy
\end{equation}

This gives:
\begin{equation}
\label{eq:phi_difference}
\int_I |f(g(y))|^2 (\phi(y)^2 - g'(y)) \, dy = 0
\end{equation}

Since this holds for all $f \in L^2(J, dx)$ and the composition $f(g(\cdot))$ generates a dense subspace of $L^2(I, g'(y) \, dy)$, the fundamental lemma of calculus of variations implies:
\begin{equation}
\label{eq:phi_ae_equal}
\phi(y)^2 = g'(y) \text{ almost everywhere}
\end{equation}

Taking $\phi(y) > 0$, one obtains $\phi(y) = \sqrt{g'(y)}$ almost everywhere.
\end{proof}

\section{Unitary Operators and Measure Preservation}

\begin{definition}[Koopman Operator]
\label{def:koopman}
Let $(X, \mathcal{B}, \mu)$ be a probability space and $T: X \to X$ be a measure-preserving bijection. The Koopman operator $U_T: L^2(X, \mu) \to L^2(X, \mu)$ is defined by:
\begin{equation}
\label{eq:koopman}
(U_T f)(x) = f(T(x))
\end{equation}
\end{definition}

\begin{theorem}[Unitarity of Koopman Operator]
\label{thm:koopman_unitary}
The Koopman operator $U_T$ defined in Definition~\ref{def:koopman} is unitary on $L^2(X, \mu)$.
\end{theorem}

\begin{proof}
For $f, h \in L^2(X, \mu)$:
\begin{align}
\langle U_T f, U_T h \rangle &= \int_X f(T(x)) \overline{h(T(x))} \, d\mu(x) \label{eq:inner_product1}\\
&= \int_X f(y) \overline{h(y)} \, d\mu(T^{-1}(y)) \label{eq:inner_product2}\\
&= \int_X f(y) \overline{h(y)} \, d\mu(y) \label{eq:inner_product3}\\
&= \langle f, h \rangle \label{eq:inner_product4}
\end{align}

where equation~\eqref{eq:inner_product2} uses the change of variables $y = T(x)$, and equation~\eqref{eq:inner_product3} follows from the measure-preserving property of $T$.

Since $T$ is bijective and measure-preserving, $U_T$ is surjective, completing the proof of unitarity.
\end{proof}

\begin{corollary}[Equivalence of Unitary Bijection and Measure Preservation]
\label{cor:unitary_equiv}
A bijective transformation $T$ on a probability space induces a unitary operator on $L^2$ if and only if $T$ is measure-preserving.
\end{corollary}

\begin{proof}
This follows directly from Theorem~\ref{thm:koopman_unitary} and the fact that the Koopman operator construction is reversible.
\end{proof}

\section{Invariant Measures}

\begin{definition}[Invariant Measure]
\label{def:invariant}
A measure $\mu$ on a measurable space $(X, \mathcal{B})$ is invariant under a transformation $T: X \to X$ if $\mu(T^{-1}(A)) = \mu(A)$ for all $A \in \mathcal{B}$.
\end{definition}

\begin{theorem}[Uniqueness of Finite Invariant Measures for Ergodic Systems]
\label{thm:invariant_unique}
Let $T: X \to X$ be an ergodic transformation on a measurable space. If finite invariant measures $\mu_1$ and $\mu_2$ exist for $T$, then $\mu_1 = c\mu_2$ for some constant $c > 0$.
\end{theorem}

\begin{proof}
The proof follows from the ergodic theorem and the fact that ergodic systems admit at most one invariant probability measure up to scaling~\cite{petersen1989ergodic}.
\end{proof}

\section{Conclusion}

The results establish that unitary bijections in $L^2$ spaces correspond precisely to measure-preserving transformations. The scaling factor $\sqrt{g'(y)}$ in Theorem~\ref{thm:l2_preservation} is both necessary and sufficient for norm preservation, providing the connection between differential geometry and functional analysis in the context of ergodic theory.

\begin{thebibliography}{9}

\bibitem{petersen1989ergodic}
K. Petersen, \emph{Ergodic Theory}, Cambridge Studies in Advanced Mathematics, Cambridge University Press, 1989.

\bibitem{halmos1956lectures}
P. R. Halmos, \emph{Lectures on Ergodic Theory}, Chelsea Publishing Company, 1956.

\bibitem{walters1982introduction}
P. Walters, \emph{An Introduction to Ergodic Theory}, Graduate Texts in Mathematics, Springer-Verlag, 1982.

\bibitem{reed1980functional}
M. Reed and B. Simon, \emph{Methods of Modern Mathematical Physics I: Functional Analysis}, Academic Press, 1980.

\end{thebibliography}

\end{document}
