\documentclass[12pt]{article}

\usepackage{amsmath,amsfonts,amssymb,amsthm,enumitem}
\usepackage{geometry}
\usepackage{hyperref}
\geometry{margin=1in}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue,
  pdfauthor={Stephen Crowley},
  pdftitle={L2 Norm Preservation Under Smooth Bijective Unbounded Substitutions}
}

% Theorem styles
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}

% Custom commands for references
\renewcommand{\eqref}[1]{(\ref{#1})}

% Title and author info
\title{L\textsuperscript{2} Norm Preservation Under Smooth Bijective Unbounded Substitutions}
\author{Stephen Crowley\thanks{July 30, 2025}}
\date{}

\begin{document}

\maketitle

\section{Introduction}

This document concerns the structure of $L^2$-norm-preserving operators induced on $L^2$ spaces by smooth, bijective, orientation-preserving substitutions $g : I \to J$ on (possibly unbounded) intervals $I, J \subseteq \mathbb{R}$. The topic is fundamental in ergodic theory and operator theory, as it precisely characterizes when a substitution operator corresponds to a unitary operator, and relates directly to the behavior of measures under measure-preserving bijections. The classical result is also crucial for understanding the behavior of the $L^2$ norm under change of variables. Canonicity and necessity of the Jacobian factor is established, and the role of unboundedness is treated from the start.

\section{Smooth Bijective Transformations and $L^2$ Norm Preservation}

\begin{definition}\label{def:bijectiveC1}
Let $I, J \subseteq \mathbb{R}$ be (possibly unbounded) open intervals. A map $g: I \to J$ is called a \emph{smooth bijection} if $g$ is:
\begin{enumerate}[label=(\roman*)]
    \item Bijection between $I$ and $J$,
    \item Differentiable on $I$ with $g'(y) > 0$ for almost every $y \in I$ (i.e., $g$ is strictly increasing except possibly on a set of Lebesgue measure zero).
\end{enumerate}
\end{definition}

\begin{lemma}[Bijectivity of Strictly Increasing Unbounded $C^1$ Maps]\label{lem:bijective_unbounded}
Let $I, J \subseteq \mathbb{R}$ be (possibly unbounded) open intervals. Suppose $g: I \to J$ is a $C^1$ function with $g'(y) > 0$ for all $y \in I$ except possibly a Lebesgue null set, and $g$ is unbounded above and below on $I$. Then $g$ is bijective onto $J = g(I)$, $g^{-1}$ exists and is also strictly increasing and differentiable a.e.
\end{lemma}

\begin{proof}
The function $g$ is strictly increasing on every subset of $I$ where $g'(y) > 0$; on the (at most measure-zero) set where $g'(y) = 0$, $g$ remains monotonic and continuous by $C^1$ regularity. Since $I$ is an interval and $g$ is continuous and strictly increasing almost everywhere, $g$ is injective by the intermediate value property of continuous strictly increasing functions.

Unboundedness of $g$ on $I$ implies that $g(I)$ is also an open interval in $\mathbb{R}$ (possibly the whole real line), so $g: I \to J$ is surjective. Thus, $g$ is bijective from $I$ onto $J = g(I)$. Its inverse $g^{-1}: J \to I$ is again continuous, strictly increasing (except possibly on a null set), and differentiable almost everywhere by the inverse function theorem.
\end{proof}

\section{Norm-Preserving Substitution Operators: Measure-Preservation and Unitarity}

\begin{theorem}[L\textsuperscript{2} Norm Preservation via Jacobian Factor]\label{thm:L2_jacobian}
Let $g: I \to J$ be a smooth bijection in the sense of Definition~\ref{def:bijectiveC1}. For any $f \in L^2(J,dx)$, define
\begin{equation}\label{eq:transformationdef}
    \widetilde{f}(y) := f(g(y)) \sqrt{g'(y)}.
\end{equation}
Then $\widetilde{f} \in L^2(I, dy)$ and
\begin{equation}\label{eq:L2normpres}
    \| \widetilde{f} \|_{L^2(I, dy)} = \| f \|_{L^2(J, dx)}.
\end{equation}
\end{theorem}

\begin{proof}
Since $g: I \to J$ is bijective, strictly increasing and differentiable almost everywhere with $g'(y) > 0$ a.e., the change of variables theorem applies (see e.g., \cite{RoydenFitzpatrick}, \cite{Folland}).

For any $f \in L^2(J, dx)$,
\begin{align}
    \| \widetilde{f} \|_{L^2(I, dy)}^2 
    &= \int_I | f(g(y)) \sqrt{g'(y)} |^2 \, dy \label{eq:normexpansion1}\\
    &= \int_I |f(g(y))|^2 g'(y) \, dy \label{eq:normexpansion2}
\end{align}
By the change of variables formula for Lebesgue integrals, for any measurable function $\varphi$ and bijective, strictly increasing $g$ as in Lemma~\ref{lem:bijective_unbounded}:
\begin{equation}\label{eq:cov}
    \int_I \varphi(g(y)) g'(y) \, dy = \int_{J} \varphi(x) \, dx.
\end{equation}
Setting $\varphi(x) = |f(x)|^2$, one obtains
\begin{equation}
    \int_I |f(g(y))|^2 g'(y) \, dy = \int_J |f(x)|^2 \, dx = \| f \|_{L^2(J,dx)}^2 \label{eq:aftercov}
\end{equation}
Thus, $\| \widetilde{f} \|_{L^2(I, dy)} = \| f \|_{L^2(J, dx)}$ as claimed.
\end{proof}

\section{Necessity and Canonicality of the Jacobian Weight}

\begin{lemma}[Density of Substitution Images]\label{lem:L2density}
Let $g: I \rightarrow J$ be as in Theorem~\ref{thm:L2_jacobian}. Then the collection $\{f \circ g : f \in L^2(J, dx) \}$ is dense in $L^2(I, g'(y)\,dy)$.
\end{lemma}
\begin{proof}
The transformation $T: L^2(J, dx) \to L^2(I, g'(y)\,dy)$ defined by $T(f) = f \circ g$ is an isometric isomorphism by the change of variables~\eqref{eq:cov}. The image of an isomorphism from a complete space is itself complete and thus dense.
\end{proof}

\begin{theorem}[Necessity of the Square Root Jacobian Factor]\label{thm:necessity}
Let $g: I \to J$ be as above. Suppose $\psi : I \to \mathbb{R}^+$ is measurable and for every $f \in L^2(J, dx)$,
\begin{equation}\label{eq:generalweight}
    \left\| f(g(\cdot)) \cdot \psi(\cdot) \right\|_{L^2(I, dy)} = \| f \|_{L^2(J, dx)}.
\end{equation}
Then $\psi(y) = \sqrt{g'(y)}$ for almost every $y \in I$.
\end{theorem}

\begin{proof}
Suppose \eqref{eq:generalweight} holds for all $f \in L^2(J, dx)$. Compute:
\begin{align}
    \int_I |f(g(y))|^2 |\psi(y)|^2 \, dy &= \|f\|_{L^2(J,dx)}^2 \notag \\
    &= \int_I |f(g(y))|^2 g'(y) \, dy \label{eq:proofcov}
\end{align}
Subtracting, for every $f$,
\begin{equation}
    \int_I |f(g(y))|^2 (|\psi(y)|^2 - g'(y)) \, dy = 0
\end{equation}
By Lemma~\ref{lem:L2density}, the set $\{f(g(y))\}$ is dense in $L^2(I, g'(y)dy)$. Thus, for every $u \in L^2(I, g'(y)dy)$,
\begin{equation}
    \int_I |u(y)|^2 (|\psi(y)|^2 - g'(y)) \, dy = 0
\end{equation}
By standard measure-theoretic arguments (cf. \cite{Folland}, p. 70), the only way for this to be true for all $u$ is for $|\psi(y)|^2 = g'(y)$ almost everywhere. Since $\psi$ is taken as non-negative, $\psi(y) = \sqrt{g'(y)}$ a.e.
\end{proof}

\section{Unitary Operators, Invariant Measures, and Measure-Preservation}

\begin{definition}[Koopman Operator]\label{def:koopman}
Let $(X, \mathcal{B}, \mu)$ be a probability measure space, $T: X \rightarrow X$ a measurable bijection, and $\mu$ a $T$-invariant measure: for all $A \in \mathcal{B}$, $\mu(T^{-1}A) = \mu(A)$. The \emph{Koopman operator} $U_T$ is defined for measurable $f : X \to \mathbb{C}$ by
\begin{equation}\label{eq:koopman}
    (U_T f)(x) = f(Tx).
\end{equation}
\end{definition}

\begin{theorem}[Unitarity Corresponds to Measure-Preservation]\label{thm:measurepreserving_unitary}
The Koopman operator $U_T$ on $L^2(X,\mu)$ is unitary if and only if $T$ is invertible and both $T$ and $T^{-1}$ preserve the measure $\mu$.
\end{theorem}

\begin{proof}
If $T$ is invertible and $\mu$ is $T$-invariant,
\[
    \|U_T f\|_{L^2(X,\mu)}^2 = \int_X |f(Tx)|^2 \, d\mu(x) = \int_X |f(x)|^2 \, d\mu(x)
\]
where the last equality is by change of variables $x = T^{-1}(y)$ and measure-preservation, so $U_T$ is an isometry. Surjectivity follows from invertibility of $T$ and surjectivity of $L^2$ composition.
Conversely, if $U_T$ is unitary, then the above identity must hold for all $f$. Choosing indicator functions of sets $A$, it follows that $\mu(T^{-1}(A)) = \mu(A)$, so $T$ preserves the measure.
\end{proof}

\section{Bibliography}
\begin{thebibliography}{99}
    \bibitem{RoydenFitzpatrick} H. L. Royden and P. M. Fitzpatrick, \emph{Real Analysis}, Fourth Edition, Pearson, 2010.
    \bibitem{Folland} G. B. Folland, \emph{Real Analysis: Modern Techniques and Their Applications}, Second Edition, Wiley, 1999.
    \bibitem{Walters} P. Walters, \emph{An Introduction to Ergodic Theory}, Springer, 1982.
    \bibitem{Halmos} P. R. Halmos, \emph{Measure Theory}, Springer, 1974.
    \bibitem{EinsiedlerWard} M. Einsiedler and T. Ward, \emph{Ergodic Theory with a View Towards Number Theory}, Springer, 2011.
\end{thebibliography}

\end{document}
