\documentclass[12pt]{article}
\usepackage{amsmath, amsfonts, amssymb}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\begin{document}

\title{A Quadratic Extremal Problem on the Dirichlet Space\thanks{In memory of Ralph P. Boas, Jr. (1912--1992).}}
\author{STEPHEN D. FISHER \\ \small Department of Mathematics, Northwestern University, Evanston, IL 60208, USA}
\date{}
\maketitle

\noindent
{\it Complex Variables}, 1995, Vol. 26, pp. 367--380 \hfill \copyright 1995 OPA (Overseas Publishers Association)\\
Reprints available directly from the publisher \hfill Amsterdam B.V. Published under license by\\
Photocopying permitted by license only \hfill Gordon and Breach Science Publishers S.A.\\
\hfill Printed in Malaysia

\vspace{1cm}

It is shown that there is a unique solution \( F \) to the problem
\[
\lambda = \sup \left\{ \text{Re} \int_\Delta F' \overline{F}' dA : \int_\Delta |F'|^2 dA \leq 1 \right\}.
\]
The function \( F \) is entire with a number of special properties. The number \( \lambda \) is the reciprocal of the smallest zero of the 0th Bessel function of the first kind.

\vspace{0.5cm}

AMS No. 30D50, 30D45, 30D10, 30C15\\
Communicated: R. P. Gilbert\\
(Received October 2, 1993)

\vspace{1cm}

\section*{INTRODUCTION}
The Dirichlet space, \( D \), on the open unit disc \( \Delta \) consists of all analytic functions \( f \)
\[
f(z) = \sum_{k=1}^\infty a_k z^k, \quad |z| < 1, \quad f(0) = 0,
\]
for which the quantity
\[
\int_\Delta |f'(z)|^2 dA(z) = \sum_{k=1}^\infty k |a_k|^2 =: \|f\|_D^2
\]
is finite. In connection with a generalization of Harnack's inequality, Boris Korenblum [2] has asked how large the quantity
\[
\lambda := \sup_{f \in D} \frac{\text{Re} \left( \sum_{k=1}^\infty a_k a_{k+1} \right)}{\sum_{k=1}^\infty k |a_k|^2}
\]
is and, if possible, to characterize all functions \( F \) which attain the value \( \lambda \) in (2). The expression in the numerator in (2) is not a linear function of \( f \) but rather quadratic; hence, the title of this paper.

It is simple to show that
\[
\sum_i a_k a_{k+1} = \int_\Delta |F'(z)|^2 dA(z).
\]

\vfill

367

\end{document}
