\documentclass{article}
\usepackage[english]{babel}
\usepackage{geometry,amsmath}
\geometry{letterpaper}

%%%%%%%%%% Start TeXmacs macros
\newcommand{\tmaffiliation}[1]{\\ #1}
\newcommand{\tmop}[1]{\ensuremath{\operatorname{#1}}}
%%%%%%%%%% End TeXmacs macros

\begin{document}

\title{Solutions to Specific Riccati Equations}

\author{
  Stephen Crowley
  \tmaffiliation{January 22, 2024}
}

\maketitle

\section{Introduction}

In this document, we explore exact solutions to specific forms of the Riccati
differential equation, particularly those involving Bessel functions. The
Riccati equation, a nonlinear ordinary differential equation, has significant
applications in various fields such as physics, engineering, and mathematics.

\section{Riccati Equation with Constant Coefficients}

Consider the Riccati equation given by
\begin{equation}
  y' = 2 y + y^2
\end{equation}
The exact solution to this equation is
\begin{equation}
  y (x) = - 2 \coth (2 x + C)
\end{equation}
where $C$ is an integration constant.

\section{Riccati Equation and Airy Functions}

Another interesting form of the Riccati equation is
\begin{equation}
  y' = y^2 + x
\end{equation}
This equation can be transformed into Airy's differential equation. By setting
$y = - u' / u$, we obtain
\begin{equation}
  u'' - xu = 0
\end{equation}
known as Airy's equation. The solution for the original Riccati equation then
depends on the Airy functions $\tmop{Ai} (x)$ and $\tmop{Bi} (x)$.

\section{Riccati Equations Involving Bessel Functions}

\subsection{Bessel Function Type}

Consider the equation
\begin{equation}
  \dot{y} (x) + y (x)^2 = \frac{1}{4} x^2
\end{equation}
The solution is expressed using Bessel functions as
\begin{equation}
  y (x) = \pm \frac{1}{2 x} - x \frac{J_1 (x)}{J_0 (x)}
\end{equation}
where $J_0$ and $J_1$ are Bessel functions of the first kind of order 0 and 1,
respectively.

\subsection{Modified Bessel Function Type}

Similarly, for the modified Bessel function type, we have
\begin{equation}
  \dot{y} (x) + y (x)^2 = - \frac{1}{4} x^2
\end{equation}
The solution in terms of modified Bessel functions is
\begin{equation}
  y (x) = \pm \frac{1}{2 x} - x \frac{I_1 (x)}{I_0 (x)}
\end{equation}
where $I_0$ and $I_1$ are modified Bessel functions of the first kind of order
0 and 1, respectively.

\section{Conclusion}

This document provided detailed solutions to specific Riccati differential
equations, illustrating their connection to classical functions like Bessel
and Airy functions. Such equations find wide applications across various
scientific and engineering disciplines.

\end{document}
