\documentclass{article}
\usepackage[english]{babel}
\usepackage{geometry,amsmath,amssymb}
\geometry{letterpaper}

\begin{document}

\title{Spectral Analysis of the Ornstein-Uhlenbeck Process on $\mathbb{R}$}

\date{}

\maketitle

\section{Covariance Function and Spectral Density}

The covariance function of the Ornstein-Uhlenbeck (OU) process is given by:
\begin{equation}
  C (x) = \sigma^2 e^{- \alpha |x|}
\end{equation}
where $\sigma^2$ is the variance and $\alpha > 0$ is the mean reversion rate.

The spectral density $S (\omega)$ is the Fourier transform of $C (x)$:
\begin{equation}
  \begin{array}{ll}
    S (\omega) & = \int_{- \infty}^{\infty} C (x) e^{- i \omega x} dx\\
    & = \sigma^2  \int_{- \infty}^{\infty} e^{- \alpha |x|} e^{- i \omega x}
    dx\\
    & = \sigma^2  \left( \int_0^{\infty} e^{- (\alpha + i \omega) x} dx +
    \int_0^{\infty} e^{- (\alpha - i \omega) x} dx \right)\\
    & = \sigma^2  \left[ \frac{1}{\alpha + i \omega} + \frac{1}{\alpha - i
    \omega} \right]\\
    & = \frac{2 \sigma^2 \alpha}{\alpha^2 + \omega^2}
  \end{array}
\end{equation}

\section{Orthogonal Polynomials}

The polynomials orthogonal with respect to the spectral density $S (\omega)$
are related to the Routh-Romanovski polynomials. Let $x = \omega / \alpha$,
then the weight function becomes:
\begin{equation}
  w (x) = \frac{1}{1 + x^2}
\end{equation}
The Routh-Romanovski polynomials $R_n (x)$ are defined by the recurrence
relation:
\begin{equation}
  \begin{array}{ll}
    R_0 (x) & = 1\\
    R_1 (x) & = x\\
    R_{n + 1} (x) & = xR_n (x) - k_n R_{n - 1} (x)  \quad \text{for } n \geq 1
  \end{array}
\end{equation}
where $k_n$ is a coefficient that can vary depending on the specific
normalization used. In some sources, $k_n = n^2$, but this may differ.

These polynomials satisfy the orthogonality relation:
\begin{equation}
  \int_{- \infty}^{\infty} R_m (x) R_n (x) w (x) dx = h_n \delta_{mn}
\end{equation}
where $h_n$ is a normalization constant and $\delta_{mn}$ is the Kronecker
delta.

The first few polynomials are:
\begin{equation}
  \begin{array}{ll}
    R_0 (x) & = 1\\
    R_1 (x) & = x\\
    R_2 (x) & = x^2 - 1\\
    R_3 (x) & = x^3 - 3 x\\
    R_4 (x) & = x^4 - 6 x^2 + 3
  \end{array}
\end{equation}
The polynomials orthogonal with respect to $S (\omega)$ are:
\begin{equation}
  P_n (\omega) = R_n  (\omega / \alpha)
\end{equation}

\section{Fourier Transforms of Orthogonal Polynomials}

The Fourier transforms of the first few Routh-Romanovski polynomials are:
\begin{equation}
  \begin{array}{ll}
    r_0 (t) & = \sqrt{2 \pi} \delta (t)\\
    r_1 (t) & = i \sqrt{2 \pi / \alpha}  \frac{d}{dt} [e^{- \alpha |t|}]\\
    r_2 (t) & = - \sqrt{2 \pi / \alpha^2}  \frac{d^2}{dt^2} [e^{- \alpha |t|}]
    - \sqrt{2 \pi} \delta (t)
  \end{array}
\end{equation}
where $\delta (t)$ is the Dirac delta function.

\section{Entropy Integral and Non-Compactness}

To show that the covariance operator of the OU process is not compact on $L^2
(\mathbb{R})$, we analyze the $\epsilon$-entropy integral.

The $\epsilon$-covering number $N (\epsilon)$ is related to the spectral
density:
\begin{equation}
  N (\epsilon) \approx \int_{- \infty}^{\infty} \max \left( 1, \sqrt{\frac{S
  (\omega)}{\epsilon^2}} \right) d \omega
\end{equation}
For large $\omega$, $S (\omega) \sim 2 \sigma^2 \alpha / \omega^2$, so:
\begin{equation}
  N (\epsilon) \approx 2 \int_0^{\infty} \max \left( 1, \frac{\sqrt{2 \sigma^2
  \alpha}}{\epsilon \omega} \right) d \omega
\end{equation}
Let $\omega_{\epsilon} = \sqrt{2 \sigma^2 \alpha} / \epsilon$. Then:
\begin{equation}
  \begin{array}{ll}
    N (\epsilon) & \approx 2 \left[ \omega_{\epsilon} +
    \int_{\omega_{\epsilon}}^{\infty} \frac{\sqrt{2 \sigma^2 \alpha}}{\epsilon
    \omega} d \omega \right]\\
    & = 2 \left[ \frac{\sqrt{2 \sigma^2 \alpha}}{\epsilon} + \frac{\sqrt{2
    \sigma^2 \alpha}}{\epsilon} \log \left( \frac{\infty}{\omega_{\epsilon}}
    \right) \right]\\
    & \approx \frac{C}{\epsilon} \log \left( \frac{1}{\epsilon} \right)
  \end{array}
\end{equation}
where $C$ is a constant depending on $\sigma$ and $\alpha$.

The $\epsilon$-entropy $H (\epsilon)$ is defined as $\log (N (\epsilon))$, so:
\begin{equation}
  H (\epsilon) \approx \log \left( \frac{C}{\epsilon} \right) + \log \left(
  \log \left( \frac{1}{\epsilon} \right) \right)
\end{equation}
The entropy integral is:
\begin{equation}
  \int_0^1 H (\epsilon) d \epsilon \approx \int_0^1 \left[ \log \left(
  \frac{C}{\epsilon} \right) + \log \left( \log \left( \frac{1}{\epsilon}
  \right) \right) \right] d \epsilon
\end{equation}
The second term causes the divergence. Using the change of variable $u = \log
(1 / \epsilon)$:
\begin{equation}
  \int_0^1 \log \left( \log \left( \frac{1}{\epsilon} \right) \right) d
  \epsilon = \int_0^{\infty} \log (u) e^{- u} du = \infty
\end{equation}
Therefore:
\begin{equation}
  \int_0^1 H (\epsilon) d \epsilon = \infty
\end{equation}
This divergence of the entropy integral demonstrates that the covariance
operator of the OU process is not compact on $L^2 (\mathbb{R})$.

\end{document}
