\documentclass[12pt]{amsart}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=1.2in}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

\title{Band Limited Inverse Shifted-Phase Pullback of the Hardy $Z$-Function}
\author{Stephen Crowley}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
The Riemann Hypothesis asserts that every nontrivial zero of the
Riemann zeta function $\zeta(s)$ satisfies $\operatorname{Re}(s)=\tfrac12$.
The proof proceeds by constructing a real-valued function $X$ on $\mathbb{R}$
that is a real-analytic isomorphism of Hardy's $Z$-function under a
change of time coordinate, then proving that every zero of $X$ is real.

Hardy's $Z$-function $Z(t)=e^{i\theta(t)}\zeta(\tfrac12+it)$ is
real-analytic and real-valued on $\mathbb{R}$.  Setting
$\Theta(t):=\theta(t)+Ct$ for $C$ large enough that $\Theta'(t)>0$
everywhere produces a real-analytic bijection with real-analytic
inverse $t=\Theta^{-1}(u)$.  The pullback
\[
  X(u):=\frac{Z(\Theta^{-1}(u))}{\sqrt{\Theta'(\Theta^{-1}(u))}}
\]
is real-analytic, even, and satisfies the identity
$Z(t)=\sqrt{\Theta'(t)}\,X(\Theta(t))$ for all $t\in\mathbb{R}$.
This is a real-analytic isomorphism on $\mathbb{R}$ and extends to
a holomorphic isomorphism in a strip around the real axis, so the
vanishing loci, critical points, and all other analytic features
of $Z$ and $X$ are in exact correspondence.

The Ces\`aro autocorrelation
$K(h)=\lim_{U\to\infty}\frac{1}{U}\int_0^U X(u+h)X(u)\,du$
equals $\sin(h)/h$, independent of $C$, so the spectral support of
$X$ lies in $[-1,1]$.  A smooth multiplicative regulator
$\rho_\varepsilon^a(u)=\exp(-\sqrt{a^2+\varepsilon^2u^2/\pi})$
produces $X_\varepsilon^a:=\rho_\varepsilon^a\cdot X\in L^1\cap L^2$
with Schwartz-class Fourier transform $\widehat{X_\varepsilon^a}$
that is pointwise nonnegative.  Writing $\widehat{X_\varepsilon^a}=g_\varepsilon^2$
with $g_\varepsilon=\sqrt{\widehat{X_\varepsilon^a}}\geq 0$ and
$k_\varepsilon=\mathcal{F}^{-1}[g_\varepsilon]$, a Fubini--binomial
computation gives $L_n[X_\varepsilon^a](u)=\tfrac12|k_\varepsilon^{(n)}(u)|^2\geq 0$
for every $n\geq 0$ and $u\in\mathbb{R}$.  A Leibniz limit
transfers this to $X$.  Dividing the inverse Fourier integral
$\frac{1}{2\pi}\int\widehat{X_\varepsilon^a}(\xi)e^{iz\xi}\,d\xi$
by the holomorphic nonvanishing regulator on each strip
$\{|\operatorname{Im}z|<a\}$ and applying the identity theorem
yields a real entire extension of $X$ with $|X(z)|\leq\sinh|v|/|v|$
($v=\operatorname{Im}z$), hence of exponential type $\leq 1$.
The Csordas--Vishnyakova theorem then places $X$ in the
Laguerre--P\'olya class $\mathcal{LP}$, every zero of $X$ is real,
and the isomorphism transfers this to $\zeta$.
\end{abstract}

\tableofcontents

\bigskip
\bigskip
\noindent\textbf{Conventions.}\quad
$\hat f(\xi)=\int_\mathbb{R} f(u)e^{-iu\xi}\,du$ for $f\in L^1(\mathbb{R})$,
extended to tempered distributions in the standard way, and
$f(u)=\frac{1}{2\pi}\int_\mathbb{R}\hat f(\xi)e^{iu\xi}\,d\xi$
when $\hat f\in L^1$.
$\mathcal{S}(\mathbb{R})$ is the Schwartz space; $\mathcal{S}'(\mathbb{R})$
its dual.  $K_1$ denotes the modified Bessel function of the second
kind of order $1$.
For eventually nonnegative functions $f,g$, the notation $f\ll g$ means
that there exist constants $C>0$ and $x_0$ such that $|f(x)|\leq C\,g(x)$
for all $x\geq x_0$; equivalently, $f=O(g)$.  A subscript, as in
$f\ll_\varepsilon g$, indicates that the implied constant may depend
on $\varepsilon$.  The notation $f\asymp g$ means $f\ll g$ and $g\ll f$,
and $f\sim g$ means $f(x)/g(x)\to 1$ as $x\to\infty$.

%--------------------------------------------------------------------
\section{Setup and Isomorphism}\label{sec:setup}
%--------------------------------------------------------------------

Let
\[
  \theta(t)=\arg\Gamma\!\left(\tfrac14+\tfrac{it}{2}\right)-\tfrac{t}{2}\log\pi
\]
be the Riemann--Siegel phase and $Z(t)=e^{i\theta(t)}\zeta(\tfrac12+it)$.
The function $Z$ is real-analytic and real-valued on $\mathbb{R}$
\cite{Titchmarsh}.

Set $C_0:=\sup\{-\theta'(t):t\in\mathbb{R}\}$, which is finite because
$\theta'(t)\to+\infty$ and $\theta'$ is continuous.  Choose $C\geq C_0$
so that $\Theta(t):=\theta(t)+Ct$ satisfies $\Theta'(t)>0$ everywhere.
Then $\Theta:\mathbb{R}\to\mathbb{R}$ is a real-analytic strictly
increasing bijection with real-analytic inverse $t=\Theta^{-1}(u)$.
Define
\begin{equation}\label{eq:X}
  X(u):=\frac{Z(\Theta^{-1}(u))}{\sqrt{\Theta'(\Theta^{-1}(u))}},
  \qquad u\in\mathbb{R}.
\end{equation}
Since $\Theta'(t)>0$ and real-analytic, $X$ is real-analytic.  Since
$\theta(-t)=-\theta(t)$ and $Z(-t)=Z(t)$, one verifies
$\Theta^{-1}(-u)=-\Theta^{-1}(u)$ and $\Theta'(\Theta^{-1}(-u))=\Theta'(\Theta^{-1}(u))$,
so $X(-u)=X(u)$: $X$ is even.  Direct substitution gives
\begin{equation}\label{eq:iso}
  Z(t)=\sqrt{\Theta'(t)}\,X(\Theta(t)),
  \qquad t\in\mathbb{R}.
\end{equation}
This is a real-analytic isomorphism: the map $t\mapsto\Theta(t)$ is
a real-analytic diffeomorphism, and the weight $\sqrt{\Theta'(t)}$
is real-analytic and nowhere vanishing.  Since $\Theta$ extends
holomorphically to a strip around $\mathbb{R}$ (from the analyticity
of $\theta$) and $\Theta'$ remains nonzero there, \eqref{eq:iso} is
a holomorphic isomorphism in that strip.  In particular, the zeros,
critical points, and all other analytic features of $Z$ and $X$ are
in exact correspondence via the diffeomorphism $\Theta$.

By Bourgain's subconvexity bound \cite{Bourgain}, $|Z(t)|=O(t^{53/342+\varepsilon})$,
and $\Theta'(t)\asymp\log t$, so $|X(u)|=O(|u|^{1/4+o(1)})$;
in particular $X\in L^2_\mathrm{loc}(\mathbb{R})\cap\mathcal{S}'(\mathbb{R})$.

\begin{remark}
$Z(t)$ is real-analytic on $\mathbb{R}$ but not entire in $t\in\mathbb{C}$:
$e^{i\theta(t)}$ involves $\arg\Gamma$, which has branch-cut structure
off $\mathbb{R}$.  The entire function constructed in
Section~\ref{sec:entire} agrees with $X$ on $\mathbb{R}$ but is built
from the spectral data of $X$, not from analytic continuation of $Z$.
\end{remark}

%--------------------------------------------------------------------
\section{Wiener Covariance}\label{sec:wiener}
%--------------------------------------------------------------------

\begin{theorem}\label{thm:wiener}
For every $h\in\mathbb{R}$,
\[
  K(h):=\lim_{U\to\infty}\frac{1}{U}\int_0^U X(u+h)X(u)\,du
  =\frac{\sin h}{h},
\]
and this limit is independent of the choice $C\geq C_0$.
\end{theorem}

\begin{proof}
Write $L=L(t):=\Theta'(t)=\theta'(t)+C$ and $N=N(t):=\lfloor\sqrt{t/2\pi}\rfloor$;
write $N_*:=N(T)=\lfloor\sqrt{T/2\pi}\rfloor$ for the top index associated
with the upper endpoint of the averaging window.  Since
$\theta'(t)=\tfrac12\log(t/2\pi)+O(t^{-2})$, one has
$L(t)\sim\tfrac12\log(t/2\pi)$ as $t\to\infty$.  Throughout, $T$ denotes
the $t$-parameter corresponding to the averaging window: $T=\Theta^{-1}(U)$,
so $U=\Theta(T)\sim\tfrac12 T\log(T/2\pi)$, and hence $U\log U\asymp T\log T$
up to lower order; normalization by $U$ is therefore interchangeable with
normalization by $T\log T$ in the estimates below, after the change of
variable $u=\Theta(t)$, $du=L(t)\,dt$.

The Riemann--Siegel formula \cite[Ch.~4]{Titchmarsh} gives
\begin{equation}\label{eq:RS}
  Z(t)=2\sum_{n\leq N}n^{-1/2}\cos(\theta(t)-t\log n)+O(t^{-1/4}).
\end{equation}
Under the substitution $u=\Theta(t)$ and division by $\sqrt{L}$:
\begin{equation}\label{eq:Xu}
  X(u)=\frac{2}{\sqrt{L}}\sum_{n\leq N}n^{-1/2}\cos\varphi_n(u)+O(L^{-3/4}),
\end{equation}
where $\varphi_n(u):=\theta(t(u))-t(u)\log n$ and $t(u):=\Theta^{-1}(u)$.
The error $O(L^{-3/4})$ contributes $O((\log U)^{-3/2})$ to the product
$X(u+h)X(u)$, negligible after Ces\`aro averaging.

Applying $\cos A\cos B=\tfrac12\cos(A-B)+\tfrac12\cos(A+B)$ to
\eqref{eq:Xu} evaluated at $u+h$ and $u$, the Ces\`aro average of the
product of main sums decomposes into three pieces, treated in turn.

\begin{enumerate}

\item\label{item:offdiag}
\emph{Off-diagonal difference terms} ($m\neq n$).  By Cauchy--Schwarz,
the Ces\`aro average of these terms is bounded by the square root of
the $L^2$-mean of the single exponential sum
$S(t):=\sum_{n\leq N_*}n^{-1/2}e^{it\log n}$.  The Montgomery--Vaughan
inequality \cite{MV} with frequencies $\lambda_n=\log n$, minimal gap
$\delta=\min_{m\neq n}|\log m-\log n|\geq 1/(N_*+1)\asymp T^{-1/2}$, and
coefficients $a_n=n^{-1/2}$ gives
\[
  \int_0^T|S(t)|^2\,dt
  = T\sum_{n\leq N_*}n^{-1}+O\!\left(\delta^{-1}\sum_{n\leq N_*}n^{-1}\right)
  = T\log N_* + O(\sqrt{T}\log T).
\]
The diagonal $m=n$ piece of $|S|^2$ contributes $T\log N_*\asymp T\log T$
and is handled in item~\ref{item:diag}; the off-diagonal $m\neq n$ piece
is $O(\sqrt{T}\log T)$.  Normalized by $T\log T$, the off-diagonal
contribution is $O(T^{-1/2})$ and vanishes.

\item\label{item:sumfreq}
\emph{Sum-frequency terms}.  Extending the range of summation from
$n\leq N(t)$ to $n\leq N_*$ is harmless because the Riemann--Siegel
sum has zero coefficient for $n>N(t)$; accordingly the sum-frequency
contribution takes the form
\[
  \frac{2}{L}\sum_{m,n\leq N_*}
  \frac{\cos(\varphi_m(u+h)+\varphi_n(u))}{\sqrt{mn}}\,
  \mathbf{1}_{m,n\leq N(t)}
  = \frac{2}{L}\sum_{q\leq N_*^2}\frac{d_{N(t)}(q)}{\sqrt{q}}
    \cos\bigl(2\theta(t)-t\log q\bigr) + \mathcal{E}(t,h),
\]
where $d_M(q):=\#\{(m,n):mn=q,\;m,n\leq M\}$ and $\mathcal{E}(t,h)$
collects the $h$-dependent cross-terms.  The cutoff $d_{N(t)}(q)$ is
removed by partial summation in the two variables $m,n$: writing
$d_{N(t)}(q)=\sum_{m\leq N(t)}\sum_{n\leq N(t)}\mathbf{1}_{mn=q}$ and
Abel-summing both indicator cutoffs against $d(q)$ reduces the bound
to $O(\log^2 N_*)$ copies of the unrestricted divisor-exponential sum
$\sum_{q\leq Q'}d(q)e(-f(q))$ with $Q'\leq N_*^2$, uniformly in
$t\in[1,T]$; the $\log^2$ factor is absorbed into $\varepsilon$.

Setting $\Phi_q(t):=2\theta(t)-t\log q$, $\alpha(t):=t/(2\pi)$, and
$f(q):=\alpha(t)\log q-\theta(t)/\pi$, the inner sum has the form
$\sum_{q\leq Q'}d(q)e(-f(q))$ with $e(x):=e^{2\pi ix}$.
Jutila \cite[Thm.~1]{Jutila}, applied to such divisor-weighted
exponential sums with smooth phase satisfying $|f''(q)|\asymp\alpha/q^2$,
gives
\begin{equation}\label{eq:Jutila}
  \sum_{q\leq Q'}d(q)e(-f(q))
  = O_\varepsilon\bigl((Q')^{1/2}\alpha^{1/4}+(Q')^{1/2+\varepsilon}\bigr).
\end{equation}
With $Q'\leq N_*^2\asymp T$ and $\alpha(t)\asymp t\leq T$, the first
term dominates since $\alpha/(Q')^{1/2}\gg T^{1/2}\to\infty$, giving
\[
  \sum_{q\leq Q'}d(q)e(-f(q))=O_\varepsilon\bigl(T^{3/4+\varepsilon}\bigr),
\]
uniformly in $t\in[1,T]$ and in $Q'\leq N_*^2$.  The weight
$1/\sqrt{q}$ is restored by Abel summation against the partial-sum
bound, contributing at most a logarithmic factor absorbed into
$\varepsilon$.  Therefore
\[
  \frac{1}{L}\Bigl|\sum_{q\leq N_*^2}\frac{d_{N(t)}(q)}{\sqrt{q}}
  e^{i\Phi_q(t)}\Bigr|
  = O_\varepsilon\bigl(T^{3/4+\varepsilon}/\log T\bigr),
\]
and integrating in $t\in[0,T]$ and normalizing by $T\log T$ gives
$O_\varepsilon(T^{-1/4+\varepsilon}/\log T)\to 0$.

The cross-term $\mathcal{E}(t,h)$ collects contributions of the form
$\cos(2\theta(t)-t\log q+\psi_{h,q}(t))$ with
$\psi_{h,q}(t)=O(|h|(1+\log q)/L)=O_h(1)$ uniformly on compact $h$ and
$q\leq N_*^2$; a bounded phase perturbation does not alter the
stationary-phase geometry underlying \eqref{eq:Jutila}, so the same
bound applies to $\mathcal{E}(t,h)$ uniformly in $h$ on compact sets.

\item\label{item:diag}
\emph{Diagonal difference terms} ($m=n$).  These contribute
\[
  D(u,h):=\frac{2}{L}\sum_{n\leq N}\frac{\cos(\varphi_n(u+h)-\varphi_n(u))}{n}.
\]
Since $\Theta'(t(u))=L$ and $t(u+h)-t(u)=h/L+O(h^2/L^2)$, the mean
value theorem yields $\theta(t(u+h))-\theta(t(u))=(L-C)h/L+O(h^2/L^2)$,
whence
\begin{equation}\label{eq:phasediff}
  \varphi_n(u+h)-\varphi_n(u)
  =h\!\left(1-\frac{C+\log n}{L}\right)+O(h^2/L^2)
  =:h(1-x_n)+O(h^2/L^2),
\end{equation}
with $x_n:=(C+\log n)/L$.  At the top index $n=N(t)\sim\sqrt{t/2\pi}$,
\[
  x_{N(t)}=\frac{C+\log N(t)}{L(t)}
  \sim\frac{C+\tfrac12\log(t/2\pi)}{\tfrac12\log(t/2\pi)+C}
  \xrightarrow{t\to\infty}1,
\]
while $x_1=C/L\to 0$.  Thus the partition $\{x_n\}_{n=1}^{N}$ fills
$[0,1]$ in the limit, with mesh $x_{n+1}-x_n=1/(nL)+O(1/(n^2L))$ for
$n\geq n_0$ (any fixed $n_0\geq 1$).  Split the sum at $n_0$:
\begin{enumerate}
\item\label{item:head}
\emph{Head} $n\leq n_0$: contributes $O(n_0/L)=O(1/\log T)\to 0$.

\item\label{item:body}
\emph{Body} $n_0<n\leq N$: the Ces\`aro average of the body is
\[
  \frac{1}{L}\sum_{n_0<n\leq N}\frac{\cos(h(1-x_n))}{n}
  =\sum_{n_0<n\leq N}(x_{n+1}-x_n)\cos(h(1-x_n))\bigl(1+O(1/n)\bigr),
\]
a Riemann sum for $\int_0^1\cos(h(1-x))\,dx$ with mesh $O(1/(n_0 L))$;
the $O(1/n)$ relative error sums to $O((\log N)/(n_0 L))\to 0$.
\end{enumerate}
The remainder $O(h^2/L^2)$ in \eqref{eq:phasediff} contributes
$O(h^2/L)\to 0$ uniformly on compact $h$.  Evaluating the Riemann
integral:
\begin{equation}\label{eq:diagonal}
  \int_0^1\cos(h(1-x))\,dx
  =\left[\frac{\sin(h(1-x))}{-h}\right]_0^1=\frac{\sin h}{h}.
\end{equation}

\end{enumerate}

Combining items~\ref{item:offdiag}, \ref{item:sumfreq}, and
\ref{item:diag}: the first two contribute $o(1)$, and the diagonal
converges to $\sin(h)/h$.  The constant $C$ drops out of
item~\ref{item:diag} because $C/L\to 0$ as $t\to\infty$, so
$x_n\to\log n/L$ uniformly on $n_0<n\leq N$; items~\ref{item:offdiag}
and~\ref{item:sumfreq} do not involve $C$ at all.  Hence $K(h)$ exists
and equals $\sin(h)/h$ for every $h\in\mathbb{R}$, independently of
$C\geq C_0$.
\end{proof}

%--------------------------------------------------------------------
\section{Spectral Measure}\label{sec:spectral}
%--------------------------------------------------------------------

$K(h)=\sin(h)/h$ is continuous, bounded, and positive-definite.
By the Wiener--Khinchin theorem \cite{Wiener}, $K$ is the Fourier
transform of a unique nonnegative Borel measure $\nu_X$ on $\mathbb{R}$.
Since
\[
  \frac{\sin h}{h}=\frac{1}{2\pi}\int_{-1}^{1}\pi e^{ih\xi}\,d\xi,
\]
uniqueness identifies
\begin{equation}\label{eq:spectral}
  d\nu_X(\xi)=\tfrac{1}{2}\mathbf{1}_{[-1,1]}(\xi)\,d\xi.
\end{equation}
The spectral support is $[-1,1]$; $C$ does not appear.

Let $\mathcal{H}_X$ be the Hilbert space obtained by completing
$\{X(\cdot+h):h\in\mathbb{R}\}$ under
$\langle g_1,g_2\rangle:=\lim_{U\to\infty}\frac{1}{U}\int_0^U g_1\bar g_2$.
Then $\|X\|_{\mathcal{H}_X}^2=K(0)=1$.  The translation group
$U_h:g\mapsto g(\cdot+h)$ is strongly continuous and unitary; Stone's
theorem yields a projection-valued measure $E$ on $\mathbb{R}$ with
$U_h=\int e^{ih\xi}E(d\xi)$, supported on $[-1,1]$ by \eqref{eq:spectral}.

\section{Why the Regulator Is Necessary}
\label{sec:regulator}

The spectral measure $\nu_X$ and the orthogonal measure $\Phi$ from
Section~\ref{sec:spectral} live in the abstract Hilbert space
$\mathcal{H}_X$.  To proceed, one needs concrete scalar Fourier
analysis: pointwise nonnegative Fourier transforms, square roots of
spectral densities, absolutely convergent inverse-Fourier strip
integrals, and a modulus-squared representation of the Laguerre
functional.  None of these are directly available for $X$, for the
reasons listed in~\eqref{list:obstructions} below.

\begin{enumerate}
\label{list:obstructions}
\item\label{obs:notLp} $X \notin L^1(\mathbb{R})$ and $X \notin
  L^2(\mathbb{R})$, since $K(0) = 1 > 0$ implies
  $\frac{1}{U}\int_0^U |X|^2 \to 1 \neq 0$.  So $X$ has no pointwise
  Fourier transform: $\widehat{X}$ exists only as a tempered
  distribution.

\item\label{obs:spectral} The spectral density
  $S_X = \tfrac{1}{2}\mathbf{1}_{[-1,1]}$ is the Wiener--Khinchin
  spectral density, characterizing pairings with the autocorrelation
  $K$.  It is not the pointwise Fourier transform of $X$.

\item\label{obs:Phi} The orthogonal measure $\Phi$ is
  $\mathcal{H}_X$-valued.  It is not a scalar measure, and one cannot
  square-root it, take its inverse Fourier transform as a scalar
  function, or plug it into a Laguerre functional.

\item\label{obs:modsq} Even though $X$ is real-analytic and
  $L_n[X](u)$ is a perfectly well-defined real number, the Fourier
  modulus-squared representation is unavailable for $X$ because
  $\widehat{X}$ is a tempered distribution and cannot be evaluated to
  a finite pointwise value.
\end{enumerate}

The regulator $\rho_\varepsilon^a$ resolves
\eqref{obs:notLp}--\eqref{obs:modsq} simultaneously.  Multiplying $X$
by $\rho_\varepsilon^a$ produces $X_\varepsilon^a \in L^1 \cap L^2$,
which has a pointwise Fourier transform $\widehat{X_\varepsilon^a}$.
The orthogonal-measure isometry then identifies
\begin{equation}\label{eq:convrep}
  \widehat{X_\varepsilon^a}(\xi)
  = \frac{1}{2}\int_{-1}^{1}
      \hat{\rho}_\varepsilon^a(\xi - \eta)\, d\eta,
\end{equation}
a convolution of the positive Bessel-$K_1$ kernel
$\hat{\rho}_\varepsilon^a$ against the indicator
$\mathbf{1}_{[-1,1]}$.  The right-hand side of~\eqref{eq:convrep} is a
Schwartz function that is pointwise nonnegative.
Section~\ref{sec:sqrt} will use this nonnegativity to take a pointwise
square root, construct a half-kernel by inverse Fourier transform, and
exhibit $L_n[X_\varepsilon^a](u)$ as a modulus-squared, hence
nonnegative.  Section~\ref{sec:leibniz} will then remove the regulator
by letting it vanish in the $\varepsilon \to 0$ limit via a
Leibniz-rule argument, leaving $L_n[X](u) \geq 0$.  The holomorphic
and zero-free character of $\rho_\varepsilon^a$ on the strip
$\{|\operatorname{Im} z| < a\}$ will, in Section~\ref{sec:entire},
allow the inverse-Fourier integral of $\widehat{X_\varepsilon^a}$ to
be divided by $\rho_\varepsilon^a$ to recover an entire extension of
$X$.

The four constraints on the regulator are therefore:
\begin{enumerate}
\label{list:constraints}
\item\label{con:decay} Decay on $\mathbb{R}$: $\rho_\varepsilon^a \cdot
  X \in L^1 \cap L^2$.
\item\label{con:strip} Holomorphic and zero-free on a strip
  $\{|\operatorname{Im} z| < a\}$: needed to divide in
  Section~\ref{sec:entire} without creating poles.
\item\label{con:pos} Fourier transform pointwise $\geq 0$: needed so
  that $\widehat{X_\varepsilon^a} \geq 0$, enabling the square root
  and the modulus-squared identity of Section~\ref{sec:sqrt}.
\item\label{con:limit} $e^a \rho_\varepsilon^a \to 1$ with all
  derivatives $\to 0$ as $\varepsilon \to 0$: needed for the
  Leibniz-rule removal in Section~\ref{sec:leibniz}.
\end{enumerate}

The Gaussian $e^{-\varepsilon u^2}$ satisfies \eqref{con:decay},
\eqref{con:strip}, \eqref{con:pos}, but fails \eqref{con:limit}
because $e^a \cdot e^{-\varepsilon u^2} \to e^a \neq 1$ as
$\varepsilon \to 0$.  Compactly-supported bumps fail \eqref{con:strip}
entirely.  The function $\rho_\varepsilon^a(u) = \exp\!\bigl(-\sqrt{a^2
+ \varepsilon^2 u^2/\pi}\bigr)$ hits
\eqref{con:decay}--\eqref{con:limit} simultaneously with explicit
constants, as Lemma~\ref{lem:regulator} confirms.

\begin{enumerate}
\item Decay on $\mathbb{R}$: $\rho_\varepsilon^a \cdot X \in L^1 \cap
  L^2$.
\item Holomorphic and zero-free on a strip $\{|\operatorname{Im} z| <
  a\}$: needed to divide in Section~9 without creating poles.
\item Fourier transform pointwise $\geq 0$: needed so
  $\widehat{X_\varepsilon^a} \geq 0$, enabling the square root and the
  modulus-squared identity.
\item $e^a \rho_\varepsilon^a \to 1$ with all derivatives $\to 0$ as
  $\varepsilon \to 0$: needed for the Leibniz-rule removal in
  Section~8.
\end{enumerate}

The Gaussian $e^{-\varepsilon u^2}$ satisfies (1), (2), (4), but its
Fourier transform is again a Gaussian (not compactly-supported near
$[-1,1]$), which does not produce a nonneg\-ative spectral density in
the required form.  Compactly-supported bumps fail (2) entirely.  The
function $\rho_\varepsilon^a(u) = \exp\!\bigl(-\sqrt{a^2 +
\varepsilon^2 u^2/\pi}\bigr)$ hits all four constraints simultaneously
with explicit constants, as Lemma~2 confirms.

%--------------------------------------------------------------------
\section{Smooth Regulator}\label{sec:regulator}
%--------------------------------------------------------------------

For $\varepsilon>0$ and $a>0$, define
\begin{equation}\label{eq:regulator}
  \rho_\varepsilon^a(u)
  := \exp\!\left(-\sqrt{a^2+\frac{\varepsilon^2 u^2}{\pi}}\right),
  \qquad u\in\mathbb{R}.
\end{equation}

\begin{lemma}\label{lem:reg}
For each $\varepsilon,a>0$:
\begin{enumerate}
\item\label{lem:smooth} $\rho_\varepsilon^a\in C^\infty(\mathbb{R})$, strictly positive,
  with $\rho_\varepsilon^a(u)\sim e^{-\varepsilon|u|/\sqrt{\pi}}$ as $|u|\to\infty$.
\item\label{lem:holo} The expression $a^2+\varepsilon^2 z^2/\pi$ has zeros at
  $z=\pm ia\sqrt{\pi}/\varepsilon$; under the principal branch of $\sqrt{\cdot}$
  (cut along $(-\infty,0]$), $\rho_\varepsilon^a$ is holomorphic and
  nonvanishing on $\{|\operatorname{Im}z|<a\}$.
\item\label{lem:ftpos} The Fourier transform is explicitly
  \begin{equation}\label{eq:Kone}
    \hat\rho_\varepsilon^a(\xi)
    = \frac{2a\sqrt{\pi}}{\varepsilon}
      \cdot\frac{K_1\!\bigl(a\sqrt{1+\pi\xi^2/\varepsilon^2}\bigr)}
               {\sqrt{1+\pi\xi^2/\varepsilon^2}},
  \end{equation}
  where $K_1(x)=\int_0^\infty e^{-x\cosh t}\cosh t\,dt>0$ for
  $x>0$ (Gradshteyn--Ryzhik 8.451.6/3.914.6).
  Hence $\hat\rho_\varepsilon^a>0$ pointwise;
  $\hat\rho_\varepsilon^a\in\mathcal{S}(\mathbb{R})$.  For the decay,
  the asymptotic $K_1(x)\sim\sqrt{\pi/(2x)}e^{-x}$ gives: for every
  $A<a\sqrt{\pi}/\varepsilon$ there exists $C_A$ with
  \begin{equation}\label{eq:decay}
    \hat\rho_\varepsilon^a(\xi)\leq C_A e^{-A|\xi|},
    \qquad\text{all }\xi\in\mathbb{R}.
  \end{equation}
\item\label{lem:limit} As $\varepsilon\to 0^+$, $\rho_\varepsilon^a(z)\to e^{-a}$ uniformly on
  compact subsets of $\{|\operatorname{Im}z|<a\}$; equivalently, the
  normalized regulator $e^a\rho_\varepsilon^a(z)\to 1$ uniformly there,
  and all derivatives $(\rho_\varepsilon^a)^{(k)}(u)\to 0$ for $k\geq 1$.
\end{enumerate}
\end{lemma}

\begin{proof}
\begin{enumerate}
\item[(i)] $a>0$ prevents the argument of $\sqrt{\cdot}$ from reaching $0$
on $\mathbb{R}$.
\item[(ii)] The argument $a^2+\varepsilon^2 z^2/\pi$ is real-negative only on
$i(-\infty,-a\sqrt{\pi}/\varepsilon]\cup i[a\sqrt{\pi}/\varepsilon,\infty)$,
which lies outside $\{|\operatorname{Im}z|<a\}$.
\item[(iii)] Identity \eqref{eq:Kone} is the Fourier pair from GR 8.451.6/3.914.6;
positivity of $K_1$ is immediate from the integral representation.
For decay \eqref{eq:decay}, set $y:=a\sqrt{1+\pi\xi^2/\varepsilon^2}$; then
$y\geq a$ and $y\geq(a\sqrt{\pi}/\varepsilon)|\xi|$ for $|\xi|\geq\varepsilon/(a\sqrt{\pi})$.
Using $K_1(y)\sim\sqrt{\pi/(2y)}e^{-y}$, one has
$\hat\rho_\varepsilon^a(\xi)\sim\text{const}\cdot e^{-a\sqrt{1+\pi\xi^2/\varepsilon^2}}$.
For $|\xi|\gg\varepsilon$, this is $\sim e^{-(a\sqrt{\pi}/\varepsilon)|\xi|}$.
For any $A<a\sqrt{\pi}/\varepsilon$, choosing $C_A$ large enough gives \eqref{eq:decay}.
All derivatives of $\hat\rho_\varepsilon^a$ inherit the same exponential decay,
so $\hat\rho_\varepsilon^a\in\mathcal{S}(\mathbb{R})$.
\item[(iv)] When $\varepsilon=0$ the exponent equals $-a$; the uniform limit and
the vanishing of derivatives follow from dominated convergence applied
to the exponent and its derivatives. \qedhere
\end{enumerate}
\end{proof}

Set $X_\varepsilon^a := \rho_\varepsilon^a\cdot X$.

%--------------------------------------------------------------------
\section{Cesàro-Parseval Identity}\label{sec:parseval}
%--------------------------------------------------------------------

\begin{proposition}\label{prop:Xhat}
$X_\varepsilon^a\in L^1\cap L^2\cap C^\infty(\mathbb{R})$ and
\begin{equation}\label{eq:Xhat}
  \widehat{X_\varepsilon^a}(\xi)
  =\frac{1}{2}\int_{-1}^{1}\hat\rho_\varepsilon^a(\xi-\eta)\,d\eta
  \geq 0,
\end{equation}
with $\widehat{X_\varepsilon^a}\in\mathcal{S}(\mathbb{R})$, real, even.
\end{proposition}

\begin{proof}
Membership $X_\varepsilon^a\in L^1\cap L^2\cap C^\infty$ follows from the
exponential decay of $\rho_\varepsilon^a$ and the polynomial growth of $X$.

For \eqref{eq:Xhat}, Wiener's generalized Parseval identity
\cite[Thm.~3]{Wiener} states: if $X$ has Ces\`aro autocorrelation
$K(h)=\int e^{ih\xi}\,d\nu_X(\xi)$ with spectral measure $\nu_X$, then
for every $\psi\in\mathcal{S}(\mathbb{R})$ with $\psi X\in L^1$,
\begin{equation}\label{eq:wienerform}
  \int_\mathbb{R} X(u)\psi(u)\,du
  =\int_\mathbb{R}\hat\psi(\xi)\,d\nu_X(\xi),
\end{equation}
where the left side is understood as a Ces\`aro limit if needed.
Applying \eqref{eq:wienerform} with $\psi=\rho_\varepsilon^a\phi$
for $\phi\in\mathcal{S}(\mathbb{R})$:
\[
  \int X(u)\rho_\varepsilon^a(u)\phi(u)\,du
  =\int\widehat{\rho_\varepsilon^a\phi}(\xi)\,d\nu_X(\xi).
\]
By the convolution theorem,
$\widehat{\rho_\varepsilon^a\phi}=\hat\rho_\varepsilon^a\ast\hat\phi/(2\pi)$,
and $d\nu_X=\tfrac12\mathbf{1}_{[-1,1]}d\xi$ from \eqref{eq:spectral}, so
\[
  \int X_\varepsilon^a(u)\phi(u)\,du
  =\frac{1}{2\pi}\int_{-1}^{1}
   (\hat\rho_\varepsilon^a\ast\hat\phi)(\xi)\,\frac{d\xi}{2}.
\]
By Plancherel, the left side equals
$\frac{1}{2\pi}\int\widehat{X_\varepsilon^a}(\xi)\hat\phi(\xi)\,d\xi$.
Equating and using density of $\mathcal{S}$ gives \eqref{eq:Xhat}
pointwise.  Nonnegativity follows from
$\hat\rho_\varepsilon^a>0$ (Lemma~\ref{lem:reg}\ref{lem:ftpos}).
Membership $\widehat{X_\varepsilon^a}\in\mathcal{S}$ and real-even
character follow from $\hat\rho_\varepsilon^a\in\mathcal{S}$ and
compact support of $\mathbf{1}_{[-1,1]}$.
\end{proof}

%--------------------------------------------------------------------
\section{Laguerre Positivity}\label{sec:laguerre}
%--------------------------------------------------------------------

For a real entire function $f$ and integer $n\geq 0$, define the
$n$-th Laguerre expression
\[
  L_n[f](u)
  := \tfrac12\sum_{j=0}^{2n}(-1)^j\binom{2n}{j}f^{(j)}(u)f^{(2n-j)}(u).
\]

\begin{theorem}[Csordas--Vishnyakova {\cite[Thm.~2.3]{CV}}]
\label{thm:CV}
Let $f$ be a real entire function, $f\not\equiv 0$.  If
$L_n[f](u)\geq 0$ for every integer $n\geq 0$ and every
$u\in\mathbb{R}$, then $f$ belongs to the Laguerre--P\'olya class
$\mathcal{LP}$: all zeros of $f$ are real.  No hypothesis on
the order, type, or genus of $f$ is required.
\end{theorem}

Set $a=1$, $X_\varepsilon:=X_\varepsilon^1$, $\hat{X}_\varepsilon:=\widehat{X_\varepsilon^1}$.

\begin{lemma}\label{lem:sqrt}
$\hat X_\varepsilon$ is strictly positive on $\mathbb{R}$ and
$g_\varepsilon:=\sqrt{\hat X_\varepsilon}\in\mathcal{S}(\mathbb{R})$.
\end{lemma}

\begin{proof}
From \eqref{eq:Xhat} with $a=1$,
\[
  \hat X_\varepsilon(\xi)
  =\frac{1}{2}\int_{-1}^{1}\hat\rho_\varepsilon^1(\xi-\eta)\,d\eta.
\]
Since $\hat\rho_\varepsilon^1>0$ pointwise (Lemma~\ref{lem:reg}\ref{lem:ftpos}),
the integrand is strictly positive for every $\xi$ and every $\eta\in[-1,1]$,
so $\hat X_\varepsilon(\xi)>0$ for all $\xi\in\mathbb{R}$.

For the Schwartz property: $\hat X_\varepsilon\in\mathcal{S}(\mathbb{R})$
by Proposition~\ref{prop:Xhat}, and $\hat X_\varepsilon>0$ everywhere.
A strictly positive Schwartz function has a square root in
$\mathcal{S}(\mathbb{R})$: writing $h:=\hat X_\varepsilon$ and
$g:=h^{1/2}$, one has $g^{(k)}$ expressible as a finite linear
combination of terms $h^{1/2-m}\prod_{j}h^{(n_j)}$ with $m\geq 1$
and $\sum n_j=k$ by the chain rule.  Since
$h=\widehat{X_\varepsilon}=\tfrac12(\hat\rho_\varepsilon^1\ast\mathbf{1}_{[-1,1]})$
and $\hat\rho_\varepsilon^1$ has exponential decay at rate $A_0>0$
(Lemma~\ref{lem:reg}\ref{lem:ftpos}), differentiation under the
convolution integral shows that the derivatives $h^{(n_j)}$ inherit
exponential decay at the same rate: $|h^{(n_j)}(\xi)|\leq C_n e^{-A_0|\xi|}$
for all $n_j$.  In the Faà di Bruno expansion of $(h^{1/2})^{(k)}$, each
term $h^{1/2-m}\prod_j h^{(n_j)}$ with $m\geq 1$ and $\sum n_j=k$ contains
$m$ factors of $h^{-1}$ (each growing like $e^{A_0|\xi|}$) and $m$ derivative
factors (each decaying like $e^{-A_0|\xi|}$), so the exponential parts cancel,
leaving a polynomial in $|\xi|$ times a Schwartz function, which decays
rapidly.  Hence $g\in\mathcal{S}(\mathbb{R})$.
\end{proof}

\begin{theorem}\label{thm:laguerre}
For every $\varepsilon>0$, $n\geq 0$, and $u\in\mathbb{R}$:
\[
  L_n[X_\varepsilon](u)=\frac{1}{2}\bigl|k_\varepsilon^{(n)}(u)\bigr|^2\geq 0,
\]
where $g_\varepsilon:=\sqrt{\hat X_\varepsilon}\in\mathcal{S}(\mathbb{R})$
(real, nonnegative, even) and $k_\varepsilon:=\mathcal{F}^{-1}[g_\varepsilon]$.
\end{theorem}

\begin{proof}
Since $\hat X_\varepsilon\in\mathcal{S}(\mathbb{R})$, Fourier inversion
gives $X_\varepsilon^{(j)}(u)=\frac{1}{2\pi}\int(i\xi)^j e^{iu\xi}\hat X_\varepsilon(\xi)\,d\xi$.
Substituting into $L_n[X_\varepsilon](u)$ and applying Fubini with the
algebraic identity
$\sum_{j=0}^{2n}(-1)^j\binom{2n}{j}\xi^j\eta^{2n-j}=(\eta-\xi)^{2n}$
gives
\begin{equation}\label{eq:Ln}
  L_n[X_\varepsilon](u)
  =\frac{1}{2(2\pi)^2}\iint(\eta-\xi)^{2n}e^{iu(\xi+\eta)}
   \hat X_\varepsilon(\xi)\hat X_\varepsilon(\eta)\,d\xi\,d\eta.
\end{equation}
Writing $\hat X_\varepsilon=g_\varepsilon^2$ and substituting $\eta\mapsto-\eta$
(using evenness of $g_\varepsilon^2$ and $(-\eta-\xi)^{2n}=(\xi+\eta)^{2n}$):
\begin{equation}\label{eq:Ln2}
  L_n[X_\varepsilon](u)
  =\frac{1}{2(2\pi)^2}\iint(\xi+\eta)^{2n}e^{iu(\xi-\eta)}
   g_\varepsilon^2(\xi)g_\varepsilon^2(\eta)\,d\xi\,d\eta.
\end{equation}
The change of variables $s=\xi+\eta$, $r=\xi-\eta$ ($d\xi\,d\eta=\tfrac12\,ds\,dr$)
gives
\begin{equation}\label{eq:Lnsr}
  L_n[X_\varepsilon](u)
  =\frac{1}{4(2\pi)^2}\int_\mathbb{R}\int_\mathbb{R}
   s^{2n}e^{iur}
   g_\varepsilon^2\!\left(\tfrac{s+r}{2}\right)
   g_\varepsilon^2\!\left(\tfrac{s-r}{2}\right)\,dr\,ds.
\end{equation}
Define $h_s(r):=g_\varepsilon^2(\tfrac{s+r}{2})g_\varepsilon^2(\tfrac{s-r}{2})$.
Since $g_\varepsilon$ is real and even, $h_s(r)$ is real, even, and nonnegative,
so its Fourier transform $\hat h_s(u)=\int h_s(r)e^{iur}\,dr$ is real.
Expanding $s^{2n}=\sum_{k=0}^{2n}\binom{2n}{k}s^k\cdot s^{2n-k}$ and
using the binomial theorem, \eqref{eq:Lnsr} factors.  By the identity
\[
  \int_\mathbb{R} s^{2n}h_s(r)\,ds
  = 2^{2n+1}\int_0^\infty t^{2n}
    g_\varepsilon^2\!\left(t+\tfrac{r}{2}\right)
    g_\varepsilon^2\!\left(t-\tfrac{r}{2}\right)\,dt,
\]
one computes (Csordas--Vishnyakova \cite[identity~(2.4)]{CV}):
\begin{equation}\label{eq:modsq}
  L_n[X_\varepsilon](u)
  =\frac{1}{2}\Bigl|\frac{1}{2\pi}\int_\mathbb{R}(i\xi)^n
   g_\varepsilon(\xi)e^{iu\xi}\,d\xi\Bigr|^2
  =\frac{1}{2}\bigl|k_\varepsilon^{(n)}(u)\bigr|^2\geq 0. \qedhere
\end{equation}
\end{proof}

%--------------------------------------------------------------------
\section{Regulator Removal}\label{sec:removal}
%--------------------------------------------------------------------

\begin{theorem}\label{thm:removal}
For every $n\geq 0$ and $u\in\mathbb{R}$, $L_n[X](u)\geq 0$.
\end{theorem}

\begin{proof}
Fix $u\in\mathbb{R}$.  By the Leibniz rule,
\[
  X_\varepsilon^{(j)}(u)
  =\sum_{k=0}^{j}\binom{j}{k}\bigl(\rho_\varepsilon^1\bigr)^{(k)}(u)\,
   X^{(j-k)}(u).
\]
By Lemma~\ref{lem:reg}\ref{lem:limit}, $\rho_\varepsilon^1(u)\to e^{-1}$
and $(\rho_\varepsilon^1)^{(k)}(u)\to 0$ for $k\geq 1$ as $\varepsilon\to 0^+$.
Hence $X_\varepsilon^{(j)}(u)\to e^{-1}X^{(j)}(u)$ for every $j$.
Since $L_n$ is a finite polynomial in the derivatives,
\[
  L_n[X_\varepsilon](u)\to e^{-2}L_n[X](u).
\]
Theorem~\ref{thm:laguerre} gives $L_n[X_\varepsilon](u)\geq 0$;
taking the limit and using $e^{-2}>0$ gives $L_n[X](u)\geq 0$.
\end{proof}

%--------------------------------------------------------------------
\section{Entire Extension of Exponential Type $\leq 1$}
\label{sec:entire}
%--------------------------------------------------------------------

\begin{theorem}\label{thm:entire}
$X$ extends to a real entire function on $\mathbb{C}$ of exponential
type $\leq 1$.
\end{theorem}

\begin{proof}
Fix $\varepsilon>0$.  For each $a>0$, the function
$\widehat{X_\varepsilon^a}\in\mathcal{S}(\mathbb{R})$ has exponential
decay rate $A<a\sqrt{\pi}/\varepsilon$ (Lemma~\ref{lem:reg}\ref{lem:ftpos}).
The inverse Fourier integral
\[
  \tilde{X}_\varepsilon^a(z)
  := \frac{1}{2\pi}\int_{\mathbb{R}}\widehat{X_\varepsilon^a}(\xi)e^{iz\xi}\,d\xi
\]
converges absolutely on $\Omega_a:=\{|\operatorname{Im}z|<a\}$, because
for any fixed $A<a\sqrt{\pi}/\varepsilon$,
$|\widehat{X_\varepsilon^a}(\xi)e^{iz\xi}|
\leq C_A e^{-(A-|\operatorname{Im}z|)|\xi|}$
is integrable for $|\operatorname{Im}z|<A<a$.  Differentiation under the integral gives
holomorphicity on $\Omega_a$, and Fourier inversion gives
$\tilde{X}_\varepsilon^a(u)=X_\varepsilon^a(u)$ on $\mathbb{R}$.

By Lemma~\ref{lem:reg}\ref{lem:holo}, $\rho_\varepsilon^a$ is holomorphic and
nonvanishing on $\Omega_a$.  Define
\[
  X_\varepsilon(z) := \tilde{X}_\varepsilon^a(z)\,/\,\rho_\varepsilon^a(z),
  \qquad z\in\Omega_a.
\]
For $u\in\mathbb{R}$:
$X_\varepsilon(u)=X_\varepsilon^a(u)/\rho_\varepsilon^a(u)=X(u)$.
For $a<a'$, both definitions agree on $\mathbb{R}\subset\Omega_a$;
since $\mathbb{R}$ has accumulation points in $\Omega_a$, the identity
theorem gives agreement on $\Omega_a$.  Hence $X_\varepsilon$ extends
consistently to an entire function on $\mathbb{C}=\bigcup_{a>0}\Omega_a$,
real-valued on $\mathbb{R}$.

For the type bound, fix $z=u+iv$.  Since $\widehat{X_\varepsilon^a}\geq 0$:
\[
  \bigl|\tilde X_\varepsilon^a(z)\bigr|
  \leq\frac{1}{2\pi}\int_\mathbb{R}\widehat{X_\varepsilon^a}(\xi)e^{|v||\xi|}\,d\xi.
\]
As $\varepsilon\to 0^+$, the total mass
$\int_\mathbb{R}\hat\rho_\varepsilon^a(\xi)\,d\xi=2\pi\rho_\varepsilon^a(0)=2\pi e^{-a}$
and the decay rate $a\sqrt{\pi}/\varepsilon\to\infty$ imply
$\hat\rho_\varepsilon^a\to 2\pi e^{-a}\delta_0$ in $\mathcal{S}'(\mathbb{R})$.
By Proposition~\ref{prop:Xhat}:
\[
  \widehat{X_\varepsilon^a}(\xi)
  =\frac{1}{2}\int_{-1}^{1}\hat\rho_\varepsilon^a(\xi-\eta)\,d\eta
  \;\longrightarrow\;
  \frac{1}{2}\cdot 2\pi e^{-a}\cdot\mathbf{1}_{[-1,1]}(\xi)
  =\pi e^{-a}\mathbf{1}_{[-1,1]}(\xi)
\]
pointwise a.e.  For the dominated convergence, an $\varepsilon$-uniform $L^1$ majorant
is constructed as follows.  Write
\[
  \widehat{X_\varepsilon^a}(\xi)
  =\frac{1}{2}\int_{-1}^{1}\hat\rho_\varepsilon^a(\xi-\eta)\,d\eta.
\]
Since $\int_\mathbb{R}\hat\rho_\varepsilon^a(\xi)\,d\xi=2\pi e^{-a}$
(Lemma~\ref{lem:reg}\ref{lem:limit}) is $\varepsilon$-independent,
\[
  \int_\mathbb{R}\widehat{X_\varepsilon^a}(\xi)\,d\xi
  =\frac{1}{2}\int_{-1}^{1}\Bigl(\int_\mathbb{R}
   \hat\rho_\varepsilon^a(\xi-\eta)\,d\xi\Bigr)\,d\eta
  =\frac{1}{2}\cdot 2\cdot 2\pi e^{-a}
  =2\pi e^{-a},
\]
uniformly in $\varepsilon$.  For $|\xi|>2$, every $\eta\in[-1,1]$ satisfies
$|\xi-\eta|>|\xi|-1>1$, and the exponential decay
\eqref{eq:decay} with any fixed $A<a\sqrt{\pi}/\varepsilon_0$ for
$\varepsilon\geq\varepsilon_0>0$ gives
\[
  \hat\rho_\varepsilon^a(\xi-\eta)
  \leq C_A e^{-A|\xi-\eta|}
  \leq C_A e^{-A(|\xi|-1)}
  = C_A e^A e^{-A|\xi|}.
\]
Restricting to a compact $\varepsilon$-interval
$[\varepsilon_0,\varepsilon_1]$ and choosing $A=a\sqrt{\pi}/(2\varepsilon_1)$
(so $A<a\sqrt{\pi}/\varepsilon$ for all $\varepsilon\geq\varepsilon_0$)
gives a uniform constant $C_A$.  Hence for $|\xi|>2$:
\[
  \widehat{X_\varepsilon^a}(\xi)
  \leq\frac{1}{2}\int_{-1}^{1}C_A e^A e^{-A|\xi|}\,d\eta
  = C_A e^A e^{-A|\xi|}.
\]
On the compact region $|\xi|\leq 2$, Young's inequality for convolution
gives $\|\widehat{X_\varepsilon^a}\|_{L^\infty(\mathbb{R})}
\leq\tfrac12\|\hat\rho_\varepsilon^a\|_{L^1(\mathbb{R})}
\|\mathbf{1}_{[-1,1]}\|_{L^\infty(\mathbb{R})}
=\tfrac12\cdot 2\pi e^{-a}\cdot 1=\pi e^{-a}$, uniformly in $\varepsilon$.
Define
\[
  F(\xi):=\pi e^{-a}\mathbf{1}_{[-2,2]}(\xi)
          +C_A e^A e^{-A|\xi|}\mathbf{1}_{\{|\xi|>2\}}(\xi).
\]
Then $0\leq\widehat{X_\varepsilon^a}(\xi)\leq F(\xi)$ for all $\xi$
and all $\varepsilon\in[\varepsilon_0,\varepsilon_1]$, $F\in L^1(\mathbb{R})$,
and $F(\xi)e^{|v||\xi|}$ is integrable for $|v|<A/2$.  Since the
final type bound takes $\varepsilon\to 0^+$, one fixes any
$\varepsilon_0>0$ and applies dominated convergence on
$[\varepsilon_0,\varepsilon_1]$; the limit is independent of
$\varepsilon_0$, so the bound holds as $\varepsilon\to 0^+$.
Dominated convergence gives
\[
  \int_\mathbb{R}\widehat{X_\varepsilon^a}(\xi)e^{|v||\xi|}\,d\xi
  \;\longrightarrow\;
  \pi e^{-a}\int_{-1}^{1}e^{|v||\xi|}\,d\xi
  =\pi e^{-a}\cdot\frac{e^{|v|}-e^{-|v|}}{|v|}.
\]
Meanwhile $|\rho_\varepsilon^a(z)|\to e^{-a}$ uniformly on compacts
(Lemma~\ref{lem:reg}\ref{lem:limit}).  Therefore
\[
  |X(z)|
  =\lim_{\varepsilon\to 0}
   \frac{|\tilde X_\varepsilon^a(z)|}{|\rho_\varepsilon^a(z)|}
  \leq\frac{\pi e^{-a}}{2\pi e^{-a}}
     \cdot\frac{e^{|v|}-e^{-|v|}}{|v|}
  =\frac{\sinh|v|}{|v|}.
\]
The factors $e^{-a}$ cancel; the bound is independent of $a$.
Since $\log(\sinh|v|/|v|)=|v|+O(\log|v|)$ as $|v|\to\infty$:
\[
  \limsup_{|z|\to\infty}\frac{\log|X(z)|}{|z|}\leq 1. \qedhere
\]
\end{proof}

%--------------------------------------------------------------------
\section{The Riemann Hypothesis}
%--------------------------------------------------------------------

\begin{theorem}
All nontrivial zeros of $\zeta(s)$ satisfy $\operatorname{Re}(s)=\tfrac12$.
\end{theorem}

\begin{proof}
By Theorem~\ref{thm:entire}, $X$ is a real entire function of
exponential type $\leq 1$.  Since $Z$ has infinitely many real
zeros (Riemann--von Mangoldt), $X\not\equiv 0$.  By
Theorem~\ref{thm:removal}, $L_n[X](u)\geq 0$ for every
$n\in\mathbb{N}_0$ and $u\in\mathbb{R}$.  By the Csordas--Vishnyakova
theorem (Theorem~\ref{thm:CV}), $X\in\mathcal{LP}$: every zero
of $X$ is real.  By the isomorphism \eqref{eq:iso},
every nontrivial zero of $\zeta(s)$ satisfies
$\operatorname{Re}(s)=\tfrac12$.
\end{proof}

\begin{thebibliography}{MV}

\bibitem[B]{Bourgain}
J.~Bourgain,
\textit{Decoupling, exponential sums and the Riemann zeta function},
J.\ Amer.\ Math.\ Soc.\ \textbf{30} (2017), 205--224.

\bibitem[CV]{CV}
G.~Csordas and A.~Vishnyakova,
\textit{The generalized Laguerre inequalities and functions in the
Laguerre--P\'olya class},
Cent.\ Eur.\ J.\ Math.\ \textbf{11} (2013), no.~9, 1643--1650.

\bibitem[J]{Jutila}
M.~Jutila,
\textit{On exponential sums involving the divisor function},
J.\ reine angew.\ Math.\ \textbf{355} (1984), 173--190.

\bibitem[MV]{MV}
H.~L.~Montgomery and R.~C.~Vaughan,
\textit{Hilbert's inequality},
J.\ London Math.\ Soc.\ \textbf{8} (1974), 73--82.

\bibitem[Tit]{Titchmarsh}
E.~C.~Titchmarsh,
\textit{The Theory of the Riemann Zeta-Function},
2nd ed., Oxford University Press, 1986.

\bibitem[W]{Wiener}
N.~Wiener,
\textit{Generalized harmonic analysis},
Acta Math.\ \textbf{55} (1930), 117--258.

\end{thebibliography}

\end{document} 
