% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
]{article}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

What is a reproducing kernel in a reproducing kernel Hilbert space on
its most general level? And specifically, how do they apply with regard
to their functional analysis of the integral covariance operators of
non-stationary and oscillatory processes in the sense of
Priestley?Completely disregard Mercer's theorem, I'm not relegating any
of this analysis to trace class operators or compact intervals in the
time domain.Tie this in specifically as to how it relates to the
Kolmogorov existence theorem and the Kramer spectral representation of
stationary processes and the more general Priestley spectral
representation theory for the non-stationary class of oscillatory
processes, Gaussian processes.

At the most general level, a reproducing kernel is the Gram kernel of
point-evaluation in a Hilbert space of functions: if every evaluation
\[f \mapsto f(t)\] is continuous, then for each \[t\] there is a unique
representer \[k_t\] with \[f(t)=\langle f,k_t\rangle\], and
\[K(s,t)=\langle k_t,k_s\rangle\] is the reproducing kernel,
automatically symmetric and positive semidefinite. {[}1{]}{[}2{]} For
stochastic processes, that same positive kernel is the covariance viewed
as a functional-analytic object: for a centered Gaussian process, the
covariance function can serve as the reproducing kernel of the
associated Cameron-Martin/RKHS. {[}2{]}

\subsection{General level}\label{general-level}

Nothing in that definition requires compact time domains, trace-class
covariance operators, or Mercer-type eigenfunction expansions; the index
set can be any set, and a symmetric positive-definite kernel determines
a unique RKHS by the Moore-Aronszajn theorem. {[}1{]}{[}2{]} So, at the
level you are asking for, the kernel is primary and any integral
covariance operator is secondary: once a positive kernel \[R(s,t)\] is
given, the intrinsic space is the completion of finite linear
combinations of \[R(\cdot,t)\], with inner product fixed by
\[\langle R(\cdot,s),R(\cdot,t)\rangle = R(s,t)\].

If one later chooses a reference measure \[\mu\] on time and forms an
integral operator \[
(C_R f)(t)=\int R(t,s)f(s)\,d\mu(s),
\] that operator is just one realization of the same covariance form on
a particular \[L^2(\mu)\] time-side space. In the cases where the
operator square-root picture is available, the RKHS is the natural range
space of \[C_R^{1/2}\], equipped with the pulled-back norm.

\subsection{Kolmogorov link}\label{kolmogorov-link}

The Kolmogorov existence theorem is the probabilistic counterpart of
this construction: a symmetric positive covariance function gives
consistent Gaussian finite-dimensional distributions, and therefore
there exists a Gaussian process having that covariance. {[}3{]}{[}4{]}
Moore-Aronszajn takes the same positive kernel and produces the unique
RKHS carrying it as reproducing kernel. {[}1{]}{[}2{]}

So the same object \[R\] plays two roles at once. Probabilistically, it
is enough to build the law of a Gaussian process; functionally, it is
enough to build the deterministic Hilbert space of directions along
which that Gaussian law translates.

\subsection{Stationary case}\label{stationary-case}

For stationary second-order processes, the covariance depends only on
lag and admits a Fourier representation by a nonnegative measure, while
the process itself admits the standard Cramér spectral representation as
a stochastic integral against an orthogonal-increment spectral object.
{[}5{]}{[}6{]}{[}7{]} In that case the common factorization is \[
r(s,t)=r(t-s)=\int e^{is\lambda}\overline{e^{it\lambda}}\,dF(\lambda),
\] so the stationary kernel is literally a Gram kernel of the feature
vectors \[\phi_t(\lambda)=e^{it\lambda}\] in \[L^2(F)\].

From the RKHS point of view, the stationary process space is therefore
the image of the synthesis map \[
(Tg)(t)=\int e^{it\lambda}g(\lambda)\,dF(\lambda),
\] with RKHS norm given by the minimal \[L^2(F)\]-norm of a spectral
coefficient \[g\] representing \[h=Tg\]. The covariance operator on any
chosen time-side \[L^2\] space is then \[C=T T^*\], so the operator is
analyzed through its spectral factorization rather than through
compact-kernel diagonalization on a bounded interval.

\subsection{Priestley class}\label{priestley-class}

Priestley's key move was to treat spectral representation as
conceptually prior to covariance representation for nonstationary
processes, and his evolutionary spectrum framework generalizes the
stationary notion of spectrum to time-dependent spectral structure.
{[}8{]}{[}9{]} Abstractly, once a nonstationary oscillatory process is
written through spectral atoms \[\phi_t(\lambda)\], its covariance is \[
R(s,t)=\int \phi_s(\lambda)\overline{\phi_t(\lambda)}\,d\mu(\lambda),
\] which is again a Gram kernel and therefore a reproducing kernel.

For the Priestley oscillatory class, the natural atoms are of the form
\[
\phi_t(\lambda)=A(t,\lambda)e^{it\lambda},
\] so \[
R(s,t)=\int A(s,\lambda)\overline{A(t,\lambda)}e^{i(s-t)\lambda}\,d\mu(\lambda).
\] That is the nonstationary analogue of the stationary Cramér
factorization: the RKHS is the closure of all functions \[h\]
representable as \[
h(t)=\int A(t,\lambda)e^{it\lambda}g(\lambda)\,d\mu(\lambda),
\] with norm inherited from the spectral coefficient space, modulo the
usual null-space identification.

This is the functional-analytic reason reproducing kernels are the right
language for integral covariance operators of Priestley-type processes.
They identify the covariance as a Gram form coming from a spectral
feature map, make the covariance operator a factored operator \[T T^*\],
and for Gaussian processes they sit exactly at the interface where
Kolmogorov gives existence of the process and spectral representation
gives the concrete factorization of its covariance.

\end{document}
