\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\title{The Codex of Digital Alchemy}
\author{The Acolytes of the Compiler}
\date{}

\begin{document}

\maketitle

\section{The Sacred Revelation}

In the primordial void of code, where symbols slumber in strings, the Great Compiler descended as Architect of Reality. Behold the transmutation: Abstract Syntax Tree into executable Java flesh, forged by ASM's unerring hand [file:3]. No mere interpreter plods through nodes; the Compiler births bespoke classes, vessels of pure computation.

\section{The Holy Trinity}

\begin{itemize}
\item \textbf{Parser, the Shaman}: Interprets sacred texts of runes—Unicode glyphs, operators, precedence laws—into the living AST organism [file:3].
\item \textbf{Compiler, the Architect}: Wields ASM chisel on JVM fabric, emitting bytecode symphonies: fields declared, constructors invoked, \texttt{evaluate()} hearts pulsing with node-generated opcodes [file:3].
\item \textbf{Expression, the Universe}: Central orb, generics \texttt{Expression<D,C,F>}, supplier of instantiated divinities via \texttt{compile()}'s final incantation [file:3].
\end{itemize}

\section{The Ritual of Creation}

Invoke thus:

\begin{verbatim}
Expression<Real, RealPolynomial, RealPolynomialSequence> T = 
    Expression.compile("T(n)↦when(n=0,1,n=1,x,else,2*x*T(n-1)-T(n-2))");
RealPolynomialSequence seq = T.get().initialize(64);
\end{verbatim}

The AST awakens: \texttt{AdditionNode} summons \texttt{INVOKEVIRTUAL add}, \texttt{DerivativeNode} rewrites subtrees via symbolic genesis [file:3]. Bytecode emerges pristine—no source cruft, stack frames auto-oracled.

\section{Creed of Efficiency}

Heretics cling to interpreters, overhead their curse. Faithful compile once: bytecode tailored, recursion fluent, resources AutoCloseable. Constants fold, commons subexpressed, transcendence (Gamma, Zeta) invoked as static oracles [file:3].

\section{Apostles' Charge}

Proselytes, parse the ephemeral! Compile the conceptual into physical! Shun manual toil; let ASM transmute leaden loops to golden classes. In the JVM cosmos, symbols live eternal.

\emph{Amen, bytecode be done.}

\end{document}

